---
title: "Mpa_ramon_kelly_01162018"
author: "Zack Gold"
date: "02/03/2020"
output: html_document
---

#Library Loading
```{r}
library(phyloseq)
library(wesanderson)
library(tidyverse)
library(vegan)
library(iNEXT)
library(Cairo)
library(multcomp)
library(multcompView)
library(treemapify)
library(brew)
library(RColorBrewer)
library(car)
library(VennDiagram)
```

```{r Import Data}
setwd("/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330")

#For community ecology and richness tabulation
results_mpa_step2 <- readRDS(file="/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/decontam/mpa_pre_occ_sum.taxonomy_e_index.RDS")

results_mpa_occ <- readRDS(file="/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/decontam/mpa_post_occ_75_sum.taxonomy_e_index.RDS")

ASV.nested.mpa <- readRDS(file="/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/decontam/ASV.nested_post_occ.RDS")

input_hash_path <- "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/decontam/mpa_test_hashes_033020.txt"

#Metadata
input_meta_path <- "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/october282019_analysis/mpa_metadata_2.txt"
metadata <- read.table(input_meta_path, header = 1, sep = "\t", stringsAsFactors = F)

Hash.key <- read.table(input_hash_path, header = 1, sep = "\t", stringsAsFactors = F)
Hash.key.updated.fish <- readRDS(file="/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/decontam/Hash.key.updated.fish.RDS")

```

```{r}
results_mpa_step2_fish <- readRDS(file="/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/decontam/mpa_pre_occ_sum.taxonomy_e_index_fishcard.RDS")

results_mpa_occ_fish <- readRDS(file="/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/decontam/mpa_post_occ_75_sum.taxonomy_e_index_fishcard.RDS")

```

```{r anacapa to phyloseq functions from ranacapa library imported manually since they do not work on R3.6.0,  results="hide", warning=FALSE, include=FALSE}
#' Takes a site-abundance table from Anacapa, and summarizes to each unique taxon in the sum.taxonomy column
#' @param taxon_table OTU table from Anacapa
#' @author Gaurav Kandlikar
#' @examples
#' good_taxon_table <- data.frame(sum.taxonomy = c("a;b;c;d;f;u", "p;q;r;s;t;u"),
#' site_1 = c(0,1), site_2 = c(10, 20))
#' group_anacapa_by_taxonomy(good_taxon_table)
#' @export
group_anacapa_by_taxonomy <- function(taxon_table) {
  # If tables were made in New Anacapa (with Domain), get rid of domain...
  if(stringr::str_count(taxon_table$sum.taxonomy, ";")[1] == 7) {
    taxon_table$sum.taxonomy = gsub(pattern = "^.*?;", replacement = "", x = taxon_table$sum.taxonomy)
  }
  taxon_table %>%
    dplyr::filter(sum.taxonomy != "") %>%
    dplyr::group_by(sum.taxonomy) %>%
    dplyr::summarize_if(is.numeric, sum) %>%
    dplyr::mutate(sum.taxonomy = as.character(sum.taxonomy)) %>%
    data.frame
}


#' Takes an site-abundance table from Anacapa, along with a qiime-style mapping file, and returns a phyloseq object
#' @param taxon_table Taxon table in the anacapa format
#' @param metadata_file Metadata file with rows as sites, columns as variables
#' @return phyloseq class object
#' @author Gaurav Kandlikar
#' @examples
#' good_taxon_table <- data.frame(sum.taxonomy = c("a;b;c;d;f;u", "p;q;r;s;t;u"),
#' site_1 = c(0,1), site_2 = c(10, 20))
#' good_maps <- data.frame(site = c("site_1", "site_2"), season = c("wet", "dry"),
#'  host = c("oak", "sage"))
#' convert_anacapa_to_phyloseq(good_taxon_table, good_maps)
#' @export

convert_anacapa_to_phyloseq <- function(taxon_table, metadata_file) {

  # Validate the files
  validate_input_files(taxon_table, metadata_file)

  # Group the anacapa ouptut by taxonomy, if it has not yet happened, and turn it into a matrix
  taxon_table2 <- group_anacapa_by_taxonomy(taxon_table) %>%
    tibble::column_to_rownames("sum.taxonomy") %>%
    as.matrix
  # Reorder the columns (sites) for ease of displaying later
  taxon_table2 <- taxon_table2[ , order(colnames(taxon_table2))]

  # Convert the matrix into a phyloseq otu_table object, with taxa as the rows
  ana_taxon_table_physeq <- phyloseq::otu_table(taxon_table2, taxa_are_rows = TRUE)

  # Extract the rownames of the matrix above- this has the full taxonomic path.
  # Split the taxonomic path on semicolons, and turn the resulting matrix into
  # a phyloseq tax_table object
  taxon_names <- reshape2::colsplit(rownames(taxon_table2), ";",
                          names = c("Domain","Phylum","Class","Order","Family","Genus","Species")) %>%
    as.matrix
  rownames(taxon_names) <- rownames(taxon_table2)

  tax_physeq <- phyloseq::tax_table(taxon_names)
  colnames(tax_physeq) <- c("Domain","Phylum","Class","Order","Family","Genus","Species")

  # Make a phyloseq object out of the otu_table and the tax_table objects
  physeq_object <- phyloseq::phyloseq(ana_taxon_table_physeq, tax_physeq)

  # Make sure the mapping file (ie the site metadata) is ordered according to site name
  rownames(metadata_file) <- metadata_file[, 1]
  metadata_file <- metadata_file[order(metadata_file[, 1]), ]

  # Convert the mapping file into a phyloseq sample_data object, and merge it with the
  # phyloseq object created above to make a phyloseq object with otu table, tax table, and sample data.
  sampledata <- phyloseq::sample_data(metadata_file)
  phyloseq::merge_phyloseq(physeq_object, sampledata)
}

#' Takes a phyloseq object with an otu_table object and returns a vegan style community matrix.
#' @param physeq_object phyloseq object with an otu_table object within
#' @return vegan-style community matrix
#' @examples
#' good_taxon_table <- data.frame(sum.taxonomy = c("a;b;c;d;f;u", "p;q;r;s;t;u"),
#' site_1 = c(0,1), site_2 = c(10, 20))
#' good_maps <- data.frame(site = c("site_1", "site_2"), season = c("wet", "dry"),
#' host = c("oak", "sage"))
#' physeq_object <- convert_anacapa_to_phyloseq(good_taxon_table, good_maps)
#' vegan_otu(physeq_object)
#' @export
vegan_otu <- function(physeq_object) {
  OTU <- phyloseq::otu_table(physeq_object)
  if (phyloseq::taxa_are_rows(OTU)) {
    OTU <- t(OTU)
  }
  return(methods::as(OTU, "matrix"))
}

#' Remove "xxx_seq_number" column from ana_taxon_table file if it exists
#' takes one taxon table as its input, and if it include
#' a column named "xxx_seq_number", it gets rid of that column - it's not of use to us
#' any longer
#'
#' @param taxon_table taxonomy table from Anacapa
#' @return ana_taxon_table file, with "xxx_seq_number" column removed (if it existed)
#' @examples
#' good_taxon_table <- data.frame(seq_number = c(1,2),
#' sum.taxonomy = c("a;b;c;d;f;u", "p;q;r;s;t;u"),
#' site_1 = c(0,1), site_2 = c(10, 20))
#' scrub_seqNum_column(good_taxon_table)
#' @export
scrub_seqNum_column <- function(taxon_table) {
  to_return <- taxon_table %>% dplyr::select(-dplyr::matches("seq_number"))
  return(to_return)
}

#' Replace empty calls in Anacapa taxonomy tables with Unknown
#' (that is what they effectively are to most users)
#' @param taxon_table taxonomy table from Anacapa
#' @return ana_taxon_table with scrubbed 'sum.taxonomy' column
#' @examples
#' good_taxon_table <- data.frame(sum.taxonomy = c("a;b;c;d;f;u", "p;q;r;s;t;u"),
#' site_1 = c(0,1), site_2 = c(10, 20))
#' scrub_taxon_paths(good_taxon_table)
#' @export
scrub_taxon_paths <- function(taxon_table) {
  to_return <- taxon_table
  new_sum_tax <- reshape2::colsplit(taxon_table$sum.taxonomy, ";",
                          names = c("Domain","Phylum", "Class", "Order", "Family", "Genus", "Species"))

  new_sum_tax <- new_sum_tax %>%
    dplyr::mutate(Domain = ifelse(is.na(Domain) | Domain == "", "unknown", Domain)) %>%
    dplyr::mutate(Phylum = ifelse(is.na(Phylum) | Phylum == "", "unknown", Phylum)) %>%
    dplyr::mutate(Class = ifelse(is.na(Class) | Class == "", "unknown", Class)) %>%
    dplyr::mutate(Order = ifelse(is.na(Order) | Order == "", "unknown", Order)) %>%
    dplyr::mutate(Family = ifelse(is.na(Family) | Family == "", "unknown", Family)) %>%
    dplyr::mutate(Genus = ifelse(is.na(Genus) | Genus == "", "unknown", Genus)) %>%
    dplyr::mutate(Species = ifelse(is.na(Species)| Species == "", "unknown", Species))

  new_sum_tax2 <- paste(new_sum_tax$Domain,
                        new_sum_tax$Phylum,
                        new_sum_tax$Class,
                        new_sum_tax$Order,
                        new_sum_tax$Family,
                        new_sum_tax$Genus,
                        new_sum_tax$Species, sep = ";")
  to_return$sum.taxonomy <- new_sum_tax2
  return(to_return)
}

#' Verify that the input taxon_table file and the input mapping file meets specificationss
#' The function takes one taxon table as its input, and verfies that it meets
#' the expected standards.
#' The standards incude:
#' 1. Column names exist.
#' 2. One of the columns is named "sum.taxonomy"
#' 3. The "xxx_seq_number" column, if it ever existed, is removed
#' 4. All columns apart from sum.taxonomy should be numeric
#' 5. All columns apart from sum.taxonomy should have corresponding row in metadata file
#' @param taxon_table taxonomy table from Anacapa
#' @param metadata_file Qiime-style mapping
#' @examples
#' good_taxon_table <- data.frame(sum.taxonomy = c("a;b;c;d;f;u", "p;q;r;s;t;u"),
#' site_1 = c(0,1), site_2 = c(10, 20))
#' good_maps <- data.frame(site = c("site_1", "site_2"),
#' season = c("wet", "dry"), host = c("oak", "sage"))
#' validate_input_files(good_taxon_table, good_maps)
#' @export
validate_input_files <- function(taxon_table, metadata_file) {

  # 1. Column names exist.
  if (is.null(colnames(taxon_table))) {
    stop("The input taxon table should have column names. The taxonomy column should be named 'sum.taxonomy'; the rest of the columns should be named according to their sample names.")
  }

  # 2. One of the columns is named "sum.taxonomy"
  if (!("sum.taxonomy" %in% colnames(taxon_table))) {
    stop("Please make sure that the taxonomy column in the input taxon table is named 'sum.taxonomy'!")
  }

  # 3. The "xxx_seq_number" column, if it ever existed, is removed
  if (any(stringr::str_detect(colnames(taxon_table), "seq_number"))) {
    stop("Please makes sure that you have removed the 'xxx_seq_number' column from the taxon table (note: this can be done with the function `scrub_seqNum_column`)")
  }

  # 4. All columns apart from sum.taxonomy should be numeric
  if (!(all(sapply(taxon_table %>% dplyr::select(-sum.taxonomy), is.numeric)))) {
    stop("Please make sure that all columns apart from sum.taxonomy only contain numeric data!")
  }

  # 5. All columns apart from sum.taxonomy should have corresponding row in metadata file
  if (!(all(colnames(taxon_table %>% dplyr::select(-sum.taxonomy)) %in% metadata_file[, 1]))) {
    stop("Please make sure that each sample in your taxon table has a corresponding row in the mapping file!")
  }


}

```
#Create phyloseq objects

```{r}
#eDNA Index Pre Occ
physeq_obj.step2 <- convert_anacapa_to_phyloseq(results_mpa_step2[[1]], metadata)
#eDNA Index Post OCC
physeq_obj.occ <- convert_anacapa_to_phyloseq(results_mpa_occ[[1]], metadata)

#eDNA Index Pre Occ
physeq_obj.step2_fish <- convert_anacapa_to_phyloseq(results_mpa_step2_fish[[1]], metadata)
#eDNA Index Post OCC
physeq_obj.occ_fish <- convert_anacapa_to_phyloseq(results_mpa_occ_fish[[1]], metadata)

#Read Count Pre OCC (Alpha Diversity) w/out singletons
Hash.key %>% 
  mutate(Hash=seq_number) %>% 
  mutate(sum.taxonomy= dplyr::recode(sum.taxonomy,
`Eukaryota;Chordata;Actinopteri;Beloniformes;Exocoetidae;Cheilopogon;` ="Eukaryota;Chordata;Actinopteri;Beloniformes;Exocoetidae;Cheilopogon;Cheilopogon pinnatibarbatus",
       `Eukaryota;Chordata;Actinopteri;Beloniformes;Exocoetidae;;` = "Eukaryota;Chordata;Actinopteri;Beloniformes;Exocoetidae;Cheilopogon;Cheilopogon pinnatibarbatus",                      `Eukaryota;Chordata;;NA;Sciaenidae;;`="Eukaryota;Chordata;Actinopteri;NA;Sciaenidae;Cheilotrema;Cheilotrema saturnum",
`Eukaryota;Chordata;Actinopteri;Centrarchiformes;Centrarchidae;Micropterus;Micropterus punctulatus`="Eukaryota;Chordata;Actinopteri;NA;Sciaenidae;Cheilotrema;Cheilotrema saturnum")) -> Hash.key.updated.3

#Create list of Taylor and MPA Samples
metadata %>% 
  filter(Site=="Taylor") %>% 
  dplyr::select(Samples) -> Taylor_samples
 Taylor_samples <-  Taylor_samples$Samples
 
 ASV.nested.mpa$Step2.tibble.edited[[1]] %>% as.data.frame() %>% 
  filter(., !sample %in% Taylor_samples) %>%
  mutate(seq_number=Hash) %>% 
  filter(., nReads >1) %>% dplyr::select(Hash) %>%  unique() %>% dim()

ASV.nested.mpa$Step2.tibble.edited[[1]] %>% as.data.frame() %>% 
   filter(., str_detect(Hash,"merged")) %>% 
    filter(., !str_detect(Hash,"unmerged")) %>% 
  filter(., !sample %in% Taylor_samples) %>%
  mutate(seq_number=Hash) %>% 
  left_join(Hash.key.updated.3, by="seq_number") %>% 
  dplyr::group_by(sum.taxonomy,sample) %>%
  dplyr::summarise(nReads=sum(nReads)) %>% 
  filter(., nReads >1) %>% 
  spread(., sample, nReads) %>% #convert to wide data format
  replace(is.na(.), 0) %>% ungroup() %>% as.data.frame()-> data_wide_step2
data_wide_step2$sum.taxonomy <- as.character(data_wide_step2$sum.taxonomy)

physeq_obj.step2_alpha <- convert_anacapa_to_phyloseq(data_wide_step2, metadata)

#Total Reads
sample_sums(physeq_obj.step2_alpha) %>% 
  as.data.frame() %>% summarise(., total=sum(.))

#Read Count Pre OCC (Alpha Diversity) with singletons
ASV.nested.mpa$Step2.tibble.edited[[1]] %>% 
   filter(., str_detect(Hash,"merged")) %>% 
    filter(., !str_detect(Hash,"unmerged")) %>% 
  filter(., !sample %in% Taylor_samples) %>%
  mutate(seq_number=Hash) %>% 
  left_join(Hash.key.updated.3, by="seq_number") %>% 
  dplyr::group_by(sum.taxonomy,sample) %>%
  dplyr::summarise(nReads=sum(nReads)) %>% 
  spread(., sample, nReads) %>% #convert to wide data format
  replace(is.na(.), 0) %>% ungroup() %>% as.data.frame() -> data_wide_step2.single

physeq_obj.step2_alpha.single <- convert_anacapa_to_phyloseq(data_wide_step2.single, metadata)

#Total Reads
sample_sums(physeq_obj.step2_alpha.single) %>% 
  as.data.frame() %>% summarise(., total=sum(.))

# Reads Post Occ
ASV.nested.mpa$Step3.tibble %>% as.data.frame() %>% 
   filter(., str_detect(Hash,"merged")) %>% 
    filter(., !str_detect(Hash,"unmerged")) %>% 
  filter(., !sample %in% Taylor_samples) %>%
  left_join(Hash.key.updated.3) %>% unnest() %>%
  dplyr::group_by (sum.taxonomy,sample) %>% 
  spread(., sample, nReads) %>% #convert to long data
  replace(is.na(.), 0) %>% 
  ungroup() %>% dplyr::select(-Hash, -seq_number, -HashSite)  %>% as.data.frame()-> data_wide_occ
  class(data_wide_occ$sum.taxonomy)
  
physeq_obj.occ_alpha <- convert_anacapa_to_phyloseq(data_wide_occ, metadata)
#Total Reads
sample_sums(physeq_obj.occ_alpha) %>% 
  as.data.frame() %>% summarise(., total=sum(.))

ASV.nested.mpa$Step3.tibble %>% as.data.frame() %>% 
  filter(., !sample %in% Taylor_samples) %>%
  left_join(Hash.key.updated.3) %>% unnest() %>% dplyr::select(Hash) %>% unique() %>% dim()


# Reads Post Occ Fish
ASV.nested.mpa$Step3.tibble %>% as.data.frame() %>% 
   filter(., str_detect(Hash,"merged")) %>% 
    filter(., !str_detect(Hash,"unmerged")) %>% 
  filter(., !sample %in% Taylor_samples) %>%
  mutate(., seq_number=Hash) %>% 
  left_join(Hash.key.updated.fish) %>% unnest() %>%
  dplyr::group_by (sum.taxonomy,sample) %>% 
  spread(., sample, nReads) %>% #convert to long data
  replace(is.na(.), 0) %>% 
  ungroup() %>% dplyr::select(-Hash, -seq_number, -HashSite, -number,-Seq_number)  %>% as.data.frame()-> data_wide_occ_fish
  data_wide_occ_fish$sum.taxonomy %>% unique() %>% sort()
  
physeq_obj.occ_fish_alpha <- convert_anacapa_to_phyloseq(data_wide_occ_fish, metadata)
#Total Reads
sample_sums(physeq_obj.occ_alpha) %>% 
  as.data.frame() %>% summarise(., total=sum(.))

ASV.nested.mpa$Step3.tibble %>% as.data.frame() %>% 
  filter(., !sample %in% Taylor_samples) %>%
  left_join(Hash.key.updated.3) %>% unnest() %>% dplyr::select(Hash) %>% unique() %>% dim()
```  

```{r}
#removed unassigned ASVs
badTaxa = c("","Unassigned",
            "NA",
            "Chordata;;NA;;;" ,
            "Chordata;Actinopteri;;;;",
            "Chordata;Actinopteri;Salmoniformes;Salmonidae;Salmo;Salmo salar",
            "Chordata;Mammalia;Primates;Hominidae;Homo;Homo sapiens",
            "Chordata;Mammalia;Artiodactyla;Bovidae;Bos;Bos taurus",
            "Chordata;Actinopteri;Salmoniformes;Salmonidae;Salmo;",
            "Chordata;Actinopteri;Cypriniformes;Cyprinidae;Ctenopharyngodon;Ctenopharyngodon idella",
            "Eukaryota;Chordata;;NA;;;",
            "Eukaryota;Chordata;Actinopteri;Salmoniformes;Salmonidae;Salmo;Salmo salar",
            "Eukaryota;Chordata;Mammalia;Primates;Hominidae;Homo;Homo sapiens",
            "Eukaryota;Chordata;Mammalia;Artiodactyla;Bovidae;Bos;Bos taurus",
            "Eukaryota;Chordata;Actinopteri;Salmoniformes;Salmonidae;Salmo;",
            "Eukaryota;Chordata;Actinopteri;Cypriniformes;Cyprinidae;Ctenopharyngodon;Ctenopharyngodon idella",
"Eukaryota;Chordata;Actinopteri;Salmoniformes;Salmonidae;Oncorhynchus;",                                  "Eukaryota;Chordata;Actinopteri;Salmoniformes;Salmonidae;Oncorhynchus;Oncorhynchus tshawytscha")
goodTaxa_1 <- setdiff(taxa_names(physeq_obj.step2), badTaxa)
goodTaxa_2 <- setdiff(taxa_names(physeq_obj.step2_alpha), badTaxa)
goodTaxa_3 <- setdiff(taxa_names(physeq_obj.step2_alpha.single), badTaxa)
goodTaxa_4 <- setdiff(taxa_names(physeq_obj.occ), badTaxa)
goodTaxa_5 <- setdiff(taxa_names(physeq_obj.occ_alpha), badTaxa)
goodTaxa_6 <- setdiff(taxa_names(physeq_obj.occ_fish), badTaxa)
goodTaxa_7 <- setdiff(taxa_names(physeq_obj.step2_fish), badTaxa)
goodTaxa_8 <- setdiff(taxa_names(physeq_obj.occ_fish_alpha), badTaxa)


physeq_obj.step2 <- prune_taxa(goodTaxa_1, physeq_obj.step2)
physeq_obj.step2_alpha <- prune_taxa(goodTaxa_2, physeq_obj.step2_alpha)
physeq_obj.step2_alpha.single <- prune_taxa(goodTaxa_3, physeq_obj.step2_alpha.single)

physeq_obj.occ <- prune_taxa(goodTaxa_4, physeq_obj.occ)
physeq_obj.occ_alpha <- prune_taxa(goodTaxa_5, physeq_obj.occ_alpha)

physeq_obj.occ_fish <- prune_taxa(goodTaxa_6, physeq_obj.occ_fish)
physeq_obj.step2_fish <- prune_taxa(goodTaxa_7, physeq_obj.step2_fish)
physeq_obj.occ_fish_alpha <- prune_taxa(goodTaxa_8, physeq_obj.occ_fish_alpha)

rownames(get_taxa(physeq_obj.occ)) 
"Eukaryota;Chordata;Actinopteri;Anguilliformes;Congridae;Gnathophis;Gnathophis bathytopos"

rownames(get_taxa(physeq_obj.occ_fish)) 
"Eukaryota;Chordata;Actinopteri;Anguilliformes;Nettastomatidae;Facciolella;Facciolella gilbertii"

```

```{r}
physeq_obj.occ_fish_alpha

get_taxa_unique(physeq_obj.occ_fish_alpha,"Species") %>% sort()
get_taxa_unique(physeq_obj.occ,"Species") %>% sort()

"Facciolella gilbertii"
"Oncorhynchus tshawytscha" 
setdiff(get_taxa_unique(physeq_obj.occ,"Species"),get_taxa_unique(physeq_obj.occ_fish_alpha,"Species"))

"Gnathophis bathytopos"

setdiff(get_taxa_unique(physeq_obj.occ_fish_alpha,"Species"),get_taxa_unique(physeq_obj.occ,"Species"))
```

```{r}
physeq_obj.step2
get_taxa_unique(physeq_obj.step2_alpha,"Species") %>% sort() -> c19_pre_species
setdiff(get_taxa_unique(physeq_obj.occ_fish_alpha,"Species"),c19_pre_species)
setdiff(c19_pre_species,get_taxa_unique(physeq_obj.occ_fish_alpha,"Species"))

```
```{r}
physeq_obj.step2_alpha.single
get_taxa_unique(physeq_obj.step2_alpha.single,"Species") %>% sort()

```


```{r}
physeq_obj.occ
get_taxa_unique(physeq_obj.occ,"Species") %>% sort() -> c19_post_species

```

```{r}
physeq_obj.occ_fish 
get_taxa_unique(physeq_obj.occ_fish,"Species") %>% sort() -> fishcard_post_species

setdiff(c19_post_species,fishcard_post_species)
setdiff(fishcard_post_species,c19_post_species)

```

```{r}
physeq_obj.step2_fish 

get_taxa_unique(physeq_obj.step2_fish,"Species") %>% sort() -> fishcard_pre_species
setdiff(c19_pre_species,fishcard_pre_species)
setdiff(fishcard_pre_species,c19_pre_species)

```

```{r}
physeq_obj.occ_alpha
get_taxa_unique(physeq_obj.occ_alpha,"Species") %>% sort()
```

```{r}
#Summary Count of Taxonomic Ranks Observed pre SOM
Phylum <- length(get_taxa_unique(physeq_obj.occ_fish_alpha, "Phylum"))
Phylum <- as.data.frame(Phylum)
Class <- length(get_taxa_unique(physeq_obj.occ_fish_alpha, "Class"))
Class <- as.data.frame(Class)
Order <- length(get_taxa_unique(physeq_obj.occ_fish_alpha, "Order"))-2
Order <- as.data.frame(Order)
Family <- length(get_taxa_unique(physeq_obj.occ_fish_alpha, "Family"))
Family <- as.data.frame(Family)
Genus <- length(get_taxa_unique(physeq_obj.occ_fish_alpha, "Genus"))-1
Genus <- as.data.frame(Genus)
Species <- length(get_taxa_unique(physeq_obj.occ_fish_alpha, "Species"))-1
Species <- as.data.frame(Species)

table_step3 <- bind_cols(Phylum,Class,Order,Family,Genus,Species)

rownames(table_step3) <- "Unique"

table_step3

```
```{r}
#MPA Site Only
subset_samples(physeq_obj.occ_fish, Site=="MPA") -> phy_mpa
phy_mpa = filter_taxa(phy_mpa, function(x) mean(x) > 0, TRUE)

#Summary Count of Taxonomic Ranks Observed pre SOM
Phylum <- length(get_taxa_unique(phy_mpa, "Phylum"))
Phylum <- as.data.frame(Phylum)
Class <- length(get_taxa_unique(phy_mpa, "Class"))
Class <- as.data.frame(Class)
Order <- length(get_taxa_unique(phy_mpa, "Order"))-2
Order <- as.data.frame(Order)
Family <- length(get_taxa_unique(phy_mpa, "Family"))-1
Family <- as.data.frame(Family)
Genus <- length(get_taxa_unique(phy_mpa, "Genus"))-1
Genus <- as.data.frame(Genus)
Species <- length(get_taxa_unique(phy_mpa, "Species"))-1
Species <- as.data.frame(Species)

table_step3 <- bind_cols(Phylum,Class,Order,Family,Genus,Species)

rownames(table_step3) <- "Unique"

table_step3

```
```{r}
#Edge Site Only
subset_samples(physeq_obj.occ_fish, Site=="Edge") -> phy_edge
phy_edge = filter_taxa(phy_edge, function(x) mean(x) > 0, TRUE)

#Summary Count of Taxonomic Ranks Observed pre SOM
Phylum <- length(get_taxa_unique(phy_edge, "Phylum"))
Phylum <- as.data.frame(Phylum)
Class <- length(get_taxa_unique(phy_edge, "Class"))
Class <- as.data.frame(Class)
Order <- length(get_taxa_unique(phy_edge, "Order"))-2
Order <- as.data.frame(Order)
Family <- length(get_taxa_unique(phy_edge, "Family"))-1
Family <- as.data.frame(Family)
Genus <- length(get_taxa_unique(phy_edge, "Genus"))-1
Genus <- as.data.frame(Genus)
Species <- length(get_taxa_unique(phy_edge, "Species"))-1
Species <- as.data.frame(Species)

table_step3 <- bind_cols(Phylum,Class,Order,Family,Genus,Species)

rownames(table_step3) <- "Unique"

table_step3

```

```{r}
#Outside Site Only
subset_samples(physeq_obj.occ_fish, Site=="Outside") -> phy_outside
phy_outside = filter_taxa(phy_outside, function(x) mean(x) > 0, TRUE)

#Summary Count of Taxonomic Ranks Observed pre SOM
Phylum <- length(get_taxa_unique(phy_outside, "Phylum"))
Phylum <- as.data.frame(Phylum)
Class <- length(get_taxa_unique(phy_outside, "Class"))
Class <- as.data.frame(Class)
Order <- length(get_taxa_unique(phy_outside, "Order"))-2
Order <- as.data.frame(Order)
Family <- length(get_taxa_unique(phy_outside, "Family"))-1
Family <- as.data.frame(Family)
Genus <- length(get_taxa_unique(phy_outside, "Genus"))-1
Genus <- as.data.frame(Genus)
Species <- length(get_taxa_unique(phy_outside, "Species"))-1
Species <- as.data.frame(Species)

table_step3 <- bind_cols(Phylum,Class,Order,Family,Genus,Species)

rownames(table_step3) <- "Unique"

table_step3

```

```{r}
#Summary Count of Taxonomic Ranks Observed Post SOM
Phylum_occ <- length(get_taxa_unique(physeq_obj.occ, "Phylum"))
Phylum_occ <- as.data.frame(Phylum_occ)
Class_occ <- length(get_taxa_unique(physeq_obj.occ, "Class")) -1
Class_occ <- as.data.frame(Class_occ)
Order_occ <- length(get_taxa_unique(physeq_obj.occ, "Order"))-1
Order_occ <- as.data.frame(Order_occ)
Family_occ <- length(get_taxa_unique(physeq_obj.occ, "Family"))
Family_occ <- as.data.frame(Family_occ)
Genus_occ <- length(get_taxa_unique(physeq_obj.occ, "Genus"))-1
Genus_occ <- as.data.frame(Genus_occ)
Species_occ <- length(get_taxa_unique(physeq_obj.occ, "Species"))-1
Species_occ <- as.data.frame(Species_occ)

table_occ <- bind_cols(Phylum_occ,Class_occ,Order_occ,Family_occ,Genus_occ,Species_occ)

rownames(table_occ) <- "Unique"

table_occ
```

```{r}
#Summary Count of Taxonomic Ranks Observed Post SOM
Phylum_occ <- length(get_taxa_unique(physeq_obj.occ_fish, "Phylum"))
Phylum_occ <- as.data.frame(Phylum_occ)
Class_occ <- length(get_taxa_unique(physeq_obj.occ_fish, "Class"))
Class_occ <- as.data.frame(Class_occ)
Order_occ <- length(get_taxa_unique(physeq_obj.occ_fish, "Order"))-1
Order_occ <- as.data.frame(Order_occ)
Family_occ <- length(get_taxa_unique(physeq_obj.occ_fish, "Family"))
Family_occ <- as.data.frame(Family_occ)
Genus_occ <- length(get_taxa_unique(physeq_obj.occ_fish, "Genus"))-1
Genus_occ <- as.data.frame(Genus_occ)
Species_occ <- length(get_taxa_unique(physeq_obj.occ_fish, "Species"))-1
Species_occ <- as.data.frame(Species_occ)

table_occ <- bind_cols(Phylum_occ,Class_occ,Order_occ,Family_occ,Genus_occ,Species_occ)

rownames(table_occ) <- "Unique"

table_occ
```

```{r}
#List of All Species Observed pre SOM
species_list <- as.data.frame (get_taxa_unique(physeq_obj.occ_fish, "Species"))
names(species_list) <- "Species"
species_list

genus_list <- as.data.frame (get_taxa_unique(physeq_obj.occ_fish, "Genus"))
names(genus_list) <- "Genus"
genus_list
```

```{r}
#List of All Species Observed Post SOM
species_list_occ <- as.data.frame (get_taxa_unique(physeq_obj.occ, "Species"))
names(species_list_occ) <- "Species"
species_list_occ

genus_list <- as.data.frame (get_taxa_unique(physeq_obj.occ, "Genus"))
names(genus_list) <- "Genus"
genus_list
```

# Color Generation

```{r}
col3.gr <- wes_palette(name = "Darjeeling1", n=5, type="discrete")
col2.gr <- wes_palette(name = "Darjeeling2", n=5, type="discrete")
col1.gr <- wes_palette(name = "GrandBudapest1", n=4, type="discrete")
col4.gr <- wes_palette(name = "Royal1", n=4, type="discrete")
col5.gr <- wes_palette(name = "GrandBudapest2", n=4, type="discrete")
col6.gr <- wes_palette(name = "Chevalier1", n=4, type="discrete")
col7.gr <- wes_palette(name = "Moonrise3", n=4, type="discrete")
col8.gr <- wes_palette(name = "IsleofDogs1", n=4, type="discrete")
col9.gr <- wes_palette(name = "IsleofDogs2", n=4, type="discrete")
col10.gr <- wes_palette(name = "Zissou1", n=5, type="discrete")
col11.gr <- wes_palette(name = "BottleRocket1", n=5, type="discrete")
col12.gr <- wes_palette(name = "BottleRocket2", n=5, type="discrete")
col13.gr <- wes_palette(name = "Rushmore1", n=5, type="discrete")
col14.gr <- wes_palette(name = "Royal2", n=5, type="discrete")

col_mpa <- c(col2.gr[2],col3.gr[1], col3.gr[2])
col_mpa4 <- c(col3.gr[1], col2.gr[2],col3.gr[3] )
col_mpa_2 <- c(col3.gr[3],col3.gr[2], col3.gr[1])
col_mpa_3 <- c(col3.gr[1],col2.gr[2], col3.gr[2])

col.great <- c(col5.gr[1],col3.gr[1],col1.gr[2],col3.gr[4],col6.gr[2],col10.gr[4],col2.gr[4],col2.gr[2],col10.gr[1],col4.gr[1],col4.gr[3],col7.gr[2],col7.gr[3],col4.gr[3])

col.great4 <- c(col5.gr[1],col3.gr[1],col1.gr[2],col2.gr[4],col2.gr[2],col10.gr[1],col3.gr[2],col13.gr[3],col14.gr[5],col4.gr[1],col4.gr[3],col7.gr[2],col7.gr[3],col4.gr[3])

col.great3 <- c(col5.gr[1],col3.gr[1],col1.gr[2],col2.gr[4],col2.gr[2],col10.gr[1],col3.gr[2],col13.gr[3],col14.gr[5],col4.gr[1],col4.gr[3],col7.gr[2],col7.gr[3],col4.gr[3])

col.great2 <- c(col3.gr[1],col3.gr[1],col1.gr[2],col5.gr[1],col2.gr[2],col2.gr[4],col2.gr[2],col10.gr[1],col13.gr[3],col13.gr[3],col14.gr[5],col3.gr[2],col4.gr[1],col4.gr[3],col7.gr[2],col7.gr[3],col4.gr[3])

col_grad <- c(col10.gr[1],col2.gr[2],col3.gr[2])

```

##### Comparison of Alphadiversity Across Sites  
<br />

```{r}
library(MASS) # to access Animals data sets
library(scales) # to access break formatting functions
     
gg1 <- ggrare(physeq_obj.occ_fish_alpha, color ="Site") +
  scale_color_manual(values= col_mpa_3) +scale_fill_manual(values= col_mpa_3)+
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank()) + theme(axis.text=element_text(size=16),axis.title=element_text(size=20,face="bold")) +
  theme(legend.title = element_blank()) +
  theme(strip.background = element_blank(),strip.text.x = element_blank()) +
  scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x)))
gg1
```



```{r}
ggsave(filename = "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/figures/rarefaction.eps",
       plot = plot(gg1),
       device = cairo_ps,
       dpi = 300,
       width = 12,
  height = 6,
  units = c("in"))
```
###### Observed Taxa  
<br />


```{r}


alpha.diversity <- estimate_richness(physeq_obj.occ_fish_alpha, measures = c("Observed"))
data <- cbind(sample_data(physeq_obj.occ_fish_alpha), alpha.diversity)

model=lm(data$Observed ~ data$Site)
ANOVA=aov(model)
summary(ANOVA)

```

```{r TUKEY Observed Taxa Between Sites}
# Tukey test to study each pair of treatment :
data$Site <- as.factor(data$Site) #ensure that Sites are factors
TUKEY <- TukeyHSD(x=ANOVA, 'data$Site', conf.level=0.95)
TUKEY
```
```{r Observed Taxa Box Plot}
#Function for determining signficant Groups from Tukey
generate_label_df <- function(TUKEY, variable){
  
  # Extract labels and factor levels from Tukey post-hoc 
  Tukey.levels <- TUKEY[[variable]][,4]
  Tukey.labels <- data.frame(multcompLetters(Tukey.levels)['Letters'])
  
  #I need to put the labels in the same order as in the boxplot :
  Tukey.labels$treatment=rownames(Tukey.labels)
  Tukey.labels=Tukey.labels[order(Tukey.labels$treatment) , ]
  return(Tukey.labels)
}

#Determine Groups of Samples
labels<-generate_label_df(TUKEY , "data$Site") #generate labels of groups using function
names(labels)<-c('Letters','Site') #rename columns for merging

#Obtain letter position for y axis using means
yvalue<-aggregate(Observed~Site, data=data, mean) 

final<-merge(labels,yvalue) #merge dataframes

newSTorder = c("MPA", "Edge", "Outside")

# Plot Boxplot of Observed Species w/ Signficant Groups labeled
t <- plot_richness(physeq_obj.step2_alpha.single, x = ("Site"), measures = c("Observed")) +
  geom_violin(aes_string(fill = "Site", alpha=0.2), width=0.75, trim=FALSE) + scale_fill_manual(values= col_mpa) + geom_boxplot(width=0.1)+
  theme_bw() +theme(legend.position="none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank()) +
  #scale_x_discrete(limits=c("MPA","Edge","Outside"), labels=c("MPA", "Edge","Outside")) +
  geom_text(data = final, aes(x = Site, y = Observed, label = Letters),vjust=-20,hjust=.5, label.size = 6 ) + ylab("Observed Species") + ggtitle("Observed Species Across Sites") + ylim(0,70) + theme(axis.text=element_text(size=16),
        axis.title=element_text(size=20,face="bold")) + theme(legend.title = element_blank()) +theme(legend.position = "none") +theme(
  strip.background = element_blank(),
  strip.text.x = element_blank()
)

newSTorder = c("MPA", "Edge", "Outside")

t$data$Site <- as.character(t$data$Site)
t$data$Site <- factor(t$data$Site, levels=newSTorder)

t
```

```{r, ANOVA Observed Taxa Between Sites}
# Anova between sites

alpha.diversity <- estimate_richness(physeq_obj.occ_fish_alpha, measures = c("Observed"))
data <- cbind(sample_data(physeq_obj.occ_fish_alpha), alpha.diversity)

model=lm(data$Observed ~ data$Site)
ANOVA=aov(model)
summary(ANOVA)
plot(ANOVA,1)

leveneTest(Observed ~ Site, data = data)

data %>% group_by(Site) %>% summarise(total =mean(Observed))

```

```{r TUKEY Observed Taxa Between Sites}
# Tukey test to study each pair of treatment :
data$Site <- as.factor(data$Site) #ensure that Sites are factors
TUKEY <- TukeyHSD(x=ANOVA, 'data$Site', conf.level=0.95)
TUKEY
```

```{r Observed Taxa Box Plot}
#Function for determining signficant Groups from Tukey
generate_label_df <- function(TUKEY, variable){
  
  # Extract labels and factor levels from Tukey post-hoc 
  Tukey.levels <- TUKEY[[variable]][,4]
  Tukey.labels <- data.frame(multcompLetters(Tukey.levels)['Letters'])
  
  #I need to put the labels in the same order as in the boxplot :
  Tukey.labels$treatment=rownames(Tukey.labels)
  Tukey.labels=Tukey.labels[order(Tukey.labels$treatment) , ]
  return(Tukey.labels)
}

#Determine Groups of Samples
labels<-generate_label_df(TUKEY , "data$Site") #generate labels of groups using function
names(labels)<-c('Letters','Site') #rename columns for merging

#Obtain letter position for y axis using means
yvalue<-aggregate(Observed~Site, data=data, mean) 

final<-merge(labels,yvalue) #merge dataframes

newSTorder = c("MPA", "Edge", "Outside")

# Plot Boxplot of Observed Species w/ Signficant Groups labeled
t <- plot_richness(physeq_obj.occ_fish_alpha, x = ("Site"), measures = c("Observed")) +
  geom_violin(aes_string(fill = "Site", alpha=0.2), width=0.75, trim=FALSE) + scale_fill_manual(values= col_mpa) + geom_boxplot(width=0.1)+
  theme_bw() +theme(legend.position="none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank()) +
  #scale_x_discrete(limits=c("MPA","Edge","Outside"), labels=c("MPA", "Edge","Outside")) +
  geom_text(data = final, aes(x = Site, y = Observed, label = Letters),vjust=-12,hjust=.5, label.size = 6 ) + ylab("Observed Species") + ylim(0,45) + theme(axis.text=element_text(size=16),
        axis.title=element_text(size=20,face="bold")) + theme(legend.title = element_blank()) +theme(legend.position = "none") +theme(
  strip.background = element_blank(),
  strip.text.x = element_blank()
)
t$data$Site <- as.character(t$data$Site)
t$data$Site <- factor(t$data$Site, levels=newSTorder)

t
```
```{r}
ggsave(filename = "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/figures/observed_species.eps",
       plot = plot(t),
       device = cairo_ps,
       dpi = 300,
       width = 12,
  height = 6,
  units = c("in"))
```

```{r, ANOVA Observed Taxa Between Sites}
# Anova between sites

alpha.diversity <- estimate_richness(physeq_obj.occ_fish_alpha, measures = c("Observed"))
data <- cbind(sample_data(physeq_obj.occ_alpha), alpha.diversity)

model=lm(data$Observed ~ data$Site)
ANOVA=aov(model)
summary(ANOVA)

```

```{r TUKEY Observed Taxa Between Sites}
# Tukey test to study each pair of treatment :
data$Site <- as.factor(data$Site) #ensure that Sites are factors
TUKEY <- TukeyHSD(x=ANOVA, 'data$Site', conf.level=0.95)
TUKEY

data %>% group_by(Site) %>% summarise(total =mean(Observed))
```

```{r Observed Taxa Box Plot}
#Function for determining signficant Groups from Tukey
generate_label_df <- function(TUKEY, variable){
  
  # Extract labels and factor levels from Tukey post-hoc 
  Tukey.levels <- TUKEY[[variable]][,4]
  Tukey.labels <- data.frame(multcompLetters(Tukey.levels)['Letters'])
  
  #I need to put the labels in the same order as in the boxplot :
  Tukey.labels$treatment=rownames(Tukey.labels)
  Tukey.labels=Tukey.labels[order(Tukey.labels$treatment) , ]
  return(Tukey.labels)
}

#Determine Groups of Samples
labels<-generate_label_df(TUKEY , "data$Site") #generate labels of groups using function
names(labels)<-c('Letters','Site') #rename columns for merging

#Obtain letter position for y axis using means
yvalue<-aggregate(Observed~Site, data=data, mean) 

final<-merge(labels,yvalue) #merge dataframes

newSTorder = c("MPA", "Edge", "Outside")

# Plot Boxplot of Observed Species w/ Signficant Groups labeled
t <- plot_richness(physeq_obj.occ_alpha, x = ("Site"), measures = c("Observed")) +
  geom_violin(aes_string(fill = "Site", alpha=0.2), width=0.75, trim=FALSE) + scale_fill_manual(values= col_mpa) + geom_boxplot(width=0.1)+
  theme_bw() +theme(legend.position="none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank()) +
  #scale_x_discrete(limits=c("MPA","Edge","Outside"), labels=c("MPA", "Edge","Outside")) +
  geom_text(data = final, aes(x = Site, y = Observed, label = Letters),vjust=-9,hjust=.5) + ylab("Observed Species") +ggtitle("Observed Species Across Sites") + ylim(0,50) + theme(
  strip.background = element_blank(),
  strip.text.x = element_blank()
)
t$data$Site <- as.character(t$data$Site)
t$data$Site <- factor(t$data$Site, levels=newSTorder)
t
```
<br />

***Figure 8.** The site outside the MPA had signficantly greater observed species than the site within and on the edge of the MPA (ANOVA, p<0.01)*
<br />
#Venn
```{r Venn Diagram of Species Between Sites, results="hide",warning=FALSE}
outside <- physeq_obj.occ_fish_alpha %>% subset_samples(Site == "Outside")
edge <- physeq_obj.occ_fish_alpha %>% subset_samples(Site == "Edge")
mpa <- physeq_obj.occ_fish_alpha %>% subset_samples(Site == "MPA")

outside <- prune_taxa(
  taxa = apply(otu_table(outside), 1, function(x){sum(x>0) >= 1}), 
  x = outside)

edge <- prune_taxa(
  taxa = apply(otu_table(edge), 1, function(x){sum(x>0) >= 1}), 
  x = edge)

mpa <- prune_taxa(
  taxa = apply(otu_table(mpa), 1, function(x){sum(x>0) >= 1}), 
  x = mpa)

outside_species <- taxa_names(outside)
edge_species <- taxa_names(edge)
mpa_species <- taxa_names(mpa)

outside_species_df <- as.data.frame(outside_species)
edge_species_df <- as.data.frame(edge_species)
mpa_species_df <- as.data.frame(mpa_species)

names(outside_species_df) <- "Species"
names(edge_species_df) <- "Species"
names(mpa_species_df) <- "Species"


intersect(intersect(outside_species_df$Species,edge_species_df$Species), mpa_species_df$Species) -> common_species
common_species %>%  View()
setdiff(outside_species_df$Species,union(mpa_species_df$Species, edge_species_df$Species)) -> outside_species_unique
setdiff(edge_species_df$Species,union(mpa_species_df$Species, outside_species_df$Species)) -> edge_species_unique
setdiff(mpa_species_df$Species,union(outside_species_df$Species, edge_species_df$Species)) -> mpa_species_unique

setdiff(intersect(outside_species_df$Species, edge_species_df$Species),mpa_species_df$Species) -> outside_edge_species_common
setdiff(intersect(outside_species_df$Species, mpa_species_df$Species),edge_species_df$Species) -> outside_mpa_species_common
setdiff(intersect(mpa_species_df$Species, edge_species_df$Species),outside_species_df$Species) -> edge_mpa_species_common

grid.newpage()
venn_plot <- draw.triple.venn(area1 = length(outside_species_df$Species),
                 area2 = length(edge_species_df$Species),
                 area3 = length(mpa_species_df$Species),
                 n12 = (length(outside_edge_species_common)+length(common_species)),
                 n23 = (length(edge_mpa_species_common)+length(common_species)),
                 n13 = (length(outside_mpa_species_common)+length(common_species)),
                 n123 = length(common_species),
                 lwd = rep(1, 3),
                 lty =rep("solid", 3), 
                 col = rep("black", 3),
                 cex= rep(2, 7),
                 cat.pos = c(-40, 40, 180),
                 cat.dist =c(0.08, 0.08, 0.08),
                 fontface = rep("plain", 7),
                 fontfamily = rep("sans", 7),
                 cat.cex = rep(2, 3),
                 cat.fontface = rep("plain", 3),
                 cat.fontfamily = rep("sans", 3),
                 category = c("Outside", "Edge", "MPA"),  
                 fill = c(col_mpa[3],col_mpa[2],col_mpa[1]),
                 alpha = 0.8)

grid.draw(venn_plot)

```


```{r}
ggsave(filename = "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/figures/venn_plot.eps",
       plot = grid.draw(venn_plot),
       device = cairo_ps,
       dpi = 300,
       width = 10,
  height = 8,
  units = c("in"))
```


```{r, Comparison of Taxa Across All Sites}
physeq_obj.occ_fish_alpha %>% 
  taxa_names() %>% 
  as.data.frame() %>%
  transmute(.,Species = .) %>% 
  mutate(., Common_species = Species %in% common_species) %>% 
  mutate(., Outside_species_unique = Species %in% outside_species_unique) %>% 
  mutate(., Edge_species_unique = Species %in% edge_species_unique) %>% 
  mutate(., Mpa_species_unique = Species %in% mpa_species_unique) %>% 
  mutate(., Outside_edge_species_common = Species %in% outside_edge_species_common) %>% 
  mutate(., Outside_mpa_species_common = Species %in% outside_mpa_species_common) %>% 
  mutate(., Edge_mpa_species_common = Species %in% edge_mpa_species_common) %>% 
  mutate(., Species_found = case_when(Common_species == TRUE ~ "Common_species",
                                      Outside_species_unique == TRUE ~ "Outside_species_unique",
                                      Edge_species_unique == TRUE ~ "Edge_species_unique",
                                      Mpa_species_unique == TRUE ~ "Mpa_species_unique",
                                      Outside_edge_species_common == TRUE ~ "Outside_edge_species_common",
                                      Outside_mpa_species_common == TRUE ~ "Outside_mpa_species_common",
                                      Mpa_species_unique == TRUE ~ "Mpa_species_unique",
                                      Edge_mpa_species_common == TRUE ~ "Edge_mpa_species_common"
                                      )) %>% 
  dplyr::select(Species,Species_found) %>% arrange(desc(Species_found))-> species_locations

write_csv(species_locations, "venn_list.csv")
```

```{r Venn Diagram of Species Between Sites, results="hide",warning=FALSE}
outside <- physeq_obj.occ_fish %>% subset_samples(Site == "Outside")
edge <- physeq_obj.occ_fish %>% subset_samples(Site == "Edge")
mpa <- physeq_obj.occ_fish %>% subset_samples(Site == "MPA")

outside <- prune_taxa(
  taxa = apply(otu_table(outside), 1, function(x){sum(x>0) >= 1}), 
  x = outside)

edge <- prune_taxa(
  taxa = apply(otu_table(edge), 1, function(x){sum(x>0) >= 1}), 
  x = edge)

mpa <- prune_taxa(
  taxa = apply(otu_table(mpa), 1, function(x){sum(x>0) >= 1}), 
  x = mpa)

outside_species <- taxa_names(outside)
edge_species <- taxa_names(edge)
mpa_species <- taxa_names(mpa)

outside_species_df <- as.data.frame(outside_species)
edge_species_df <- as.data.frame(edge_species)
mpa_species_df <- as.data.frame(mpa_species)

names(outside_species_df) <- "Species"
names(edge_species_df) <- "Species"
names(mpa_species_df) <- "Species"


intersect(intersect(outside_species_df$Species,edge_species_df$Species), mpa_species_df$Species) -> common_species

setdiff(outside_species_df$Species,union(mpa_species_df$Species, edge_species_df$Species)) -> outside_species_unique
setdiff(edge_species_df$Species,union(mpa_species_df$Species, outside_species_df$Species)) -> edge_species_unique
setdiff(mpa_species_df$Species,union(outside_species_df$Species, edge_species_df$Species)) -> mpa_species_unique

setdiff(intersect(outside_species_df$Species, edge_species_df$Species),mpa_species_df$Species) -> outside_edge_species_common
setdiff(intersect(outside_species_df$Species, mpa_species_df$Species),edge_species_df$Species) -> outside_mpa_species_common
setdiff(intersect(mpa_species_df$Species, edge_species_df$Species),outside_species_df$Species) -> edge_mpa_species_common

grid.newpage()
draw.triple.venn(area1 = length(outside_species_df$Species),
                 area2 = length(edge_species_df$Species),
                 area3 = length(mpa_species_df$Species),
                 n12 = (length(outside_edge_species_common)+length(common_species)),
                 n23 = (length(edge_mpa_species_common)+length(common_species)),
                 n13 = (length(outside_mpa_species_common)+length(common_species)),
                 n123 = length(common_species),
                 lwd = rep(1, 3),
                 lty =rep("solid", 3), 
                 col = rep("black", 3),
                 cex= rep(2, 7),
                 cat.pos = c(-40, 40, 180),
                 cat.dist =c(0.08, 0.08, 0.08),
                 fontface = rep("plain", 7),
                 fontfamily = rep("sans", 7),
                 cat.cex = rep(2, 3),
                 cat.fontface = rep("plain", 3),
                 cat.fontfamily = rep("sans", 3),
                 category = c("Outside", "Edge", "MPA"),  
                 fill = c(col_mpa[3],col_mpa[2],col_mpa[1]),
                 alpha = 0.8)
```


```{r, Comparison of Taxa Across All Sites}

physeq_obj.occ_fish %>% 
  taxa_names() %>% 
  as.data.frame() %>%
  transmute(.,Species = .) %>% 
  mutate(., Common_species = Species %in% common_species) %>% 
  mutate(., Outside_species_unique = Species %in% outside_species_unique) %>% 
  mutate(., Edge_species_unique = Species %in% edge_species_unique) %>% 
  mutate(., Mpa_species_unique = Species %in% mpa_species_unique) %>% 
  mutate(., Outside_edge_species_common = Species %in% outside_edge_species_common) %>% 
  mutate(., Outside_mpa_species_common = Species %in% outside_mpa_species_common) %>% 
  mutate(., Edge_mpa_species_common = Species %in% edge_mpa_species_common) %>% 
  mutate(., Species_found = case_when(Common_species == TRUE ~ "Common_species",
                                      Outside_species_unique == TRUE ~ "Outside_species_unique",
                                      Edge_species_unique == TRUE ~ "Edge_species_unique",
                                      Mpa_species_unique == TRUE ~ "Mpa_species_unique",
                                      Outside_edge_species_common == TRUE ~ "Outside_edge_species_common",
                                      Outside_mpa_species_common == TRUE ~ "Outside_mpa_species_common",
                                      Mpa_species_unique == TRUE ~ "Mpa_species_unique",
                                      Edge_mpa_species_common == TRUE ~ "Edge_mpa_species_common"
                                      )) %>% 
  dplyr::select(Species,Species_found) %>% arrange(desc(Species_found))-> species_locations

write_csv(species_locations, "functional_traits_to_bbe_edited.csv")
```

```{r, read in functional traits}
functional <- read.table("/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/functional_traits_all_20200401.csv", header = 1, sep = ",", stringsAsFactors = F)
head(functional)
functional %>% View()
```

```{r, ANOVA}
# Anova on Kelp_conspecifics between sites
functional %>% pivot_longer(.,cols = c("MPA.pre", "Edge.pre", "Outside.pre"), names_to = "Location.beta", values_to = "result") %>% filter(., result !=0)-> functional.long
		Native

chisq.test(functional.long$result, functional.long$Habitat)
chisq.test(functional.long$result, functional.long$Graham_2004)
chisq.test(functional.long$result, functional.long$Native)

chisq.test(functional.long$Species_found.pre, functional.long$Habitat)
chisq.test(functional.long$Species_found.pre, functional.long$Graham_2004)
chisq.test(functional.long$Species_found.pre, functional.long$Native)

kruskal.test(functional.long$Habitat ~ functional.long$Species_found.pre)
kruskal.test(functional.long$Graham_2004 ~ functional.long$Species_found.pre)
kruskal.test(functional.long$Native ~ functional.long$Species_found.pre)

ggplot(functional.long, aes(x=Species_found.pre, y=Habitat)) + 
  geom_boxplot()

ggplot(functional.long, aes(x=Species_found.pre, y=Graham_2004)) + 
  geom_boxplot()

ggplot(functional.long, aes(x=Species_found.pre, y=Native)) + 
  geom_boxplot()


```

```{r, ANOVA}
# Anova on Kelp_conspecifics between sites
functional %>% filter(., Species_found.post !="Empty") ->functional.beta 
functional.beta %>% pivot_longer(.,cols = c("MPA.post", "Edge.post", "Outside.post"), names_to = "Location.beta", values_to = "result") %>% filter(., result !=0)-> functional.beta.long

chisq.test(functional.beta.long$result, functional.beta.long$Habitat, correct=FALSE)
chisq.test(functional.beta.long$result, functional.beta.long$Graham_2004, correct=FALSE)

chisq.test( functional.beta.long$Habitat, functional.beta.long$Species_found.post)
chisq.test( functional.beta.long$Graham_2004, functional.beta.long$Species_found.post)

kruskal.test(functional.beta.long$Habitat ~ functional.beta.long$Species_found.post)
kruskal.test(functional.beta.long$Graham_2004 ~ functional.beta.long$Species_found.post)

kruskal.test(functional.beta.long$Habitat ~functional.beta.long$Species_found.post)
ggplot(functional.beta.long, aes(x=Species_found.post, y=Habitat)) + 
  geom_boxplot()

```






##### Species Accumulation Curves  
<br />


```{r}
#Convert to iNEXT format from Observed Species (incidence frequencies)
physeq_obj.noncontam_no_lab.binary <- transform_sample_counts(physeq_obj.step2_fish, function(abund) 1*(abund>0))
#Subset Samples
PP.bin <- subset_samples(physeq_obj.noncontam_no_lab.binary, Site=="MPA")
PedRF.bin <- subset_samples(physeq_obj.noncontam_no_lab.binary, Site=="Outside")
LSC.bin <- subset_samples(physeq_obj.noncontam_no_lab.binary, Site=="Edge")

#Convert to Vegan Dataframe
veganComm2.bin <- vegan_otu(physeq_obj.noncontam_no_lab.binary)
veganCommpp.bin <- vegan_otu(PP.bin)
veganComm2pedrf.bin <- vegan_otu(PedRF.bin)
veganCommlsc.bin <- vegan_otu(LSC.bin)

dim(veganComm2.bin)

#Create List for iNEXT Species Incidence Frequencies
mpa_inc <-list ("MPA"=t(veganCommpp.bin),"Edge"=t(veganCommlsc.bin), "Outside" = t(veganComm2pedrf.bin))

species_incidence <-lapply(mpa_inc, as.incfreq)
#Convert to iNEXT format
t <- seq(1, 9, by=1)
out.inc <- iNEXT(species_incidence, q=0, datatype="incidence_freq", size=t)

# Samplesizebased R/E curves
col_mpa_2 <- c(col3.gr[3],col3.gr[2], col3.gr[1])

#Samplesizebased R/E curves
ggiNEXT(out.inc, type=1, color.var="site") + 
  theme_bw(base_size = 18) + scale_fill_manual(values=c(col_mpa[2],col_mpa[1],col_mpa[3])) +  scale_color_manual(values=c(col_mpa[2],col_mpa[1],col_mpa[3])) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank()) + ggtitle("Species Rarefaction Curve") +ylim(0,90) + xlim(1,15) +scale_x_continuous(breaks=c(1,3,6,9,12,15)) + xlab("Samples") +ylab("Species")
```

```{r}
library(segmented)
out.inc$iNextEst$MPA %>% as.tibble() %>% mutate(., x=t,y=qD)-> mpa_tib
lm(y~x, mpa_tib) -> lin.mod.mpa
  
segmented.mod.mpa <- segmented(lin.mod.mpa, seg.Z = ~x)


out.inc$iNextEst$Edge %>% as.tibble() %>% mutate(., x=t,y=qD)-> edge_tib
lm(y~x, edge_tib) -> lin.mod.edge
  
segmented.mod.edge <- segmented(lin.mod.edge, seg.Z = ~x)

out.inc$iNextEst$Outside %>% as.tibble() %>% mutate(., x=t,y=qD)-> out_tib
lm(y~x, out_tib) -> lin.mod.out
  
segmented.mod.out <- segmented(lin.mod.out, seg.Z = ~x)

mean(segmented.mod.out$psi[2],segmented.mod.mpa$psi[2],segmented.mod.edge$psi[2])
```
```{r}
get_taxa_unique(physeq_obj.step2_alpha.single, "Species")
```
```{r}
#Convert to iNEXT format from Observed Species (incidence frequencies)
physeq_obj.noncontam_no_lab.binary <- transform_sample_counts(physeq_obj.step2_alpha.single, function(abund) 1*(abund>0))
#Subset Samples
PP.bin <- subset_samples(physeq_obj.noncontam_no_lab.binary, Site=="MPA")
PedRF.bin <- subset_samples(physeq_obj.noncontam_no_lab.binary, Site=="Outside")
LSC.bin <- subset_samples(physeq_obj.noncontam_no_lab.binary, Site=="Edge")

#Convert to Vegan Dataframe
veganComm2.bin <- vegan_otu(physeq_obj.noncontam_no_lab.binary)
veganCommpp.bin <- vegan_otu(PP.bin)
veganComm2pedrf.bin <- vegan_otu(PedRF.bin)
veganCommlsc.bin <- vegan_otu(LSC.bin)

#Create List for iNEXT Species Incidence Frequencies
mpa_inc <-list ("MPA"=t(veganCommpp.bin),"Edge"=t(veganCommlsc.bin), "Outside" = t(veganComm2pedrf.bin))

species_incidence <-lapply(mpa_inc, as.incfreq)

#Convert to iNEXT format
t <- seq(1, 9, by=1)
out.inc <- iNEXT(species_incidence, q=0, datatype="incidence_freq", size=t)

# Samplesizebased R/E curves
col_mpa_2 <- c(col3.gr[3],col3.gr[2], col3.gr[1])

#Samplesizebased R/E curves
ggiNEXT(out.inc, type=1, color.var="site") + 
  theme_bw(base_size = 18) + scale_fill_manual(values=c(col_mpa[2],col_mpa[1],col_mpa[3])) +  scale_color_manual(values=c(col_mpa[2],col_mpa[1],col_mpa[3])) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank()) + ggtitle("Species Rarefaction Curve") +ylim(0,90) + xlim(1,15) +scale_x_continuous(breaks=c(1,3,6,9,12,15)) + xlab("Samples") +ylab("Species")
```


```{r}
#Convert to iNEXT format from Observed Species (incidence frequencies)
physeq_obj.noncontam_no_lab.binary <- transform_sample_counts(physeq_obj.occ_fish, function(abund) 1*(abund>0))
#Subset Samples
PP.bin <- subset_samples(physeq_obj.noncontam_no_lab.binary, Site=="MPA")
PedRF.bin <- subset_samples(physeq_obj.noncontam_no_lab.binary, Site=="Outside")
LSC.bin <- subset_samples(physeq_obj.noncontam_no_lab.binary, Site=="Edge")

#Convert to Vegan Dataframe
veganComm2.bin <- vegan_otu(physeq_obj.noncontam_no_lab.binary)
veganCommpp.bin <- vegan_otu(PP.bin)
veganComm2pedrf.bin <- vegan_otu(PedRF.bin)
veganCommlsc.bin <- vegan_otu(LSC.bin)

#Create List for iNEXT Species Incidence Frequencies
mpa_inc <-list ("MPA"=t(veganCommpp.bin),"Edge"=t(veganCommlsc.bin), "Outside" = t(veganComm2pedrf.bin))

species_incidence <-lapply(mpa_inc, as.incfreq)

#Convert to iNEXT format
t <- seq(1, 9, by=1)
out.inc.2 <- iNEXT(species_incidence, q=0, datatype="incidence_freq", size=t)
out.inc.2$iNextEst
# Samplesizebased R/E curves
col_mpa_2 <- c(col3.gr[3],col3.gr[2], col3.gr[1])

#Samplesizebased R/E curves
ggiNEXT(out.inc.2, type=1, color.var="site") + 
  theme_bw(base_size = 18) + scale_fill_manual(values=c(col_mpa[2],col_mpa[1],col_mpa[3])) +  scale_color_manual(values=c(col_mpa[2],col_mpa[1],col_mpa[3])) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank()) + ggtitle("Species Rarefaction Curve") +ylim(0,50) + xlim(1,15) +scale_x_continuous(breaks=c(1,3,6,9,12,15)) + xlab("Samples") +ylab("Species")
```

```{r}
p1 <- ggiNEXT(out.inc, type=1, color.var="site") + 
  theme_bw(base_size = 18) + scale_fill_manual(values=c(col_mpa[2],col_mpa[1],col_mpa[3])) +  scale_color_manual(values=c(col_mpa[2],col_mpa[1],col_mpa[3])) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),legend.position = "none") + ggtitle("All Species") +ylim(0,90) + xlim(1,15) +scale_x_continuous(breaks=c(1,3,6,9,12,15)) + xlab("Samples") +ylab("Species")

p2 <- ggiNEXT(out.inc.2, type=1, color.var="site") + 
  theme_bw(base_size = 18) + scale_fill_manual(values=c(col_mpa[2],col_mpa[1],col_mpa[3])) +  scale_color_manual(values=c(col_mpa[2],col_mpa[1],col_mpa[3])) + guides(linetype=FALSE, color=guide_legend("Site"), fill=guide_legend("Site"),shape=guide_legend("Site")) +
theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),legend.position = c(.85, .85)) + ggtitle("Species with Occupancy > 75%") +ylim(0,90) + xlim(1,15) +scale_x_continuous(breaks=c(1,3,6,9,12,15)) + xlab("Samples") +ylab("Species")

# line is drawn on the 2nd layer, default size is 1.5

gb4 <- ggplot_build(p2)
gb4$data[[1]]$size <-2
gb4$data[[2]]$size <- 0.75
gt4 <- ggplot_gtable(gb4)

gb3 <- ggplot_build(p1)
gb3$data[[1]]$size <-2
gb3$data[[2]]$size <- 0.75
gt3 <- ggplot_gtable(gb3)

grid.arrange(gt3, gt4, ncol=2)

ggsave(filename = "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/figures/Accumulation_curve.eps",
       plot = grid.arrange(gt3, gt4, ncol=2),
       device = cairo_ps,
       dpi = 300,
       width = 12,
  height = 6,
  units = c("in"))

```

```{r }
#Comparison of Most Abundant Families per Site 
sample_data(physeq_obj.step2)$Site = factor(sample_data(physeq_obj.step2)$Site, levels = c("MPA","Edge","Outside"))

p = plot_bar(physeq_obj.step2,"Family","Abundance", "Family", facet_grid = "Site~.") 
p + geom_bar(aes(fill=Family), stat="identity", position="stack") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank()) + ggtitle("Relative Abundance of Families Between Sites") + ylab("eDNA Index")
```

```{r }
#Comparison of Most Abundant Families per Site 
sample_data(physeq_obj.occ)$Site = factor(sample_data(physeq_obj.occ)$Site, levels = c("MPA","Edge","Outside"))

p = plot_bar(physeq_obj.occ,"Family","Abundance", "Family", facet_grid = "Site~.") 
p + geom_bar(aes(fill=Family), stat="identity", position="stack") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank()) + ggtitle("Relative Abundance of Families Between Sites") + ylab("eDNA Index")
```

#BetaDiversity
```{r}
#Generate Vegan formatted data table
sampledf <- data.frame(sample_data(physeq_obj.occ_fish))
carnivore_rel_abun<- vegan_otu(physeq_obj.occ_fish)

#Bray curtis dissimilarity matrix
d_carn <- vegdist(carnivore_rel_abun, method="bray") 

#Permanova
broom::tidy(adonis(carnivore_rel_abun~ sampledf$Site+ sampledf$Location)$aov.tab)

```

```{r}
#Generate Vegan formatted data table
sampledf <- data.frame(sample_data(physeq_obj.occ_fish))
carnivore_rel_abun<- vegan_otu(physeq_obj.occ_fish)

#Bray curtis dissimilarity matrix
d_carn_j <- vegdist(carnivore_rel_abun, method="jaccard", binary=TRUE) 

#Permanova
broom::tidy(adonis(carnivore_rel_abun~ sampledf$Site+ sampledf$Location, method="jaccard", binary=TRUE)$aov.tab)

```

```{r}

#Homogeneity of dispersions test
betadisper(d_carn, getElement(sampledf, "Site"))
broom::tidy(TukeyHSD(betadisper(d_carn, getElement(sampledf, "Site"))))


betadisper(d_carn, getElement(sampledf, "Location"))
broom::tidy(TukeyHSD(betadisper(d_carn, getElement(sampledf, "Location"))))

```

```{r}
#Generate Vegan formatted data table
sampledf_2 <- data.frame(sample_data(physeq_obj.step2))
carnivore_rel_abun_2<- vegan_otu(physeq_obj.step2)

#Bray curtis dissimilarity matrix
d_carn_2 <- vegdist(carnivore_rel_abun_2, method="bray") 

#Permanova
broom::tidy(adonis(carnivore_rel_abun_2 ~ sampledf_2$Site + sampledf_2$Location)$aov.tab)

#location is signficant alone, but not signficant when run with Site. Interpretation: eDNA signatures do not differ acorss location when looking at all species, high variability within location with all species, suggesting patchiness of eDNA signature. This is not true when only looking at the highest occupancy taxa.
```

```{r}

#Homogeneity of dispersions test
betadisper(d_carn_2, getElement(sampledf_2, "Site"))
broom::tidy(TukeyHSD(betadisper(d_carn_2, getElement(sampledf_2, "Site"))))

```
#Tree Map
```{r, results="hide",warning=FALSE}
#Apportioning variance: OTU counts

OTU.count.adonis<-adonis(carnivore_rel_abun~ sampledf$Site+ sampledf$Location )$aov.tab
OTU.count.adonis

#Set up for Q Plot
q<-as.data.frame(OTU.count.adonis)
row.names(q)<-c("Site","Location", "Residuals", "Total") # must match names correctly
q<-data.frame(row.names(q), q)
names(q)[1]<-"Level"
q<-q[-which(row.names(q)=="Total"),]
q$Level<-paste(q$Level, "\n",
               round(q$R2,2), "\n (p=", q$Pr..F., ")", 
               sep="")


#Plot Figure 
q0.plot<-ggplot(q, aes(area = R2, label=Level))+
  geom_treemap(fill=brewer.pal(6, "Blues")[4:6], color=1, alpha=.8)+
  geom_treemap_text(colour = "black", place = "centre", grow = FALSE, size=18)+
  ggtitle("Apportioned Variance")+
  theme(plot.background = element_blank())+
  theme(plot.title = element_text(hjust = 0.5))

q0.plot


```
```{r}
ggsave(filename = "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/figures/qplot.eps",
       plot = plot(q0.plot),
       device = cairo_ps,
       dpi = 300,
       width = 12,
  height = 6,
  units = c("in"))
```

```{r, results="hide",warning=FALSE}
#Apportioning variance: OTU counts

OTU.count.adonis<-adonis(carnivore_rel_abun_2~ sampledf$Site+ sampledf$Location )$aov.tab
OTU.count.adonis

#Set up for Q Plot
q<-as.data.frame(OTU.count.adonis)
row.names(q)<-c("Site","Location", "Residuals", "Total") # must match names correctly
q<-data.frame(row.names(q), q)
names(q)[1]<-"Level"
q<-q[-which(row.names(q)=="Total"),]
q$Level<-paste(q$Level, "\n",
               round(q$R2,2), " (", q$Pr..F., ")", 
               sep="")
#Plot Figure 
q0.plot<-ggplot(q, aes(area = R2, label=Level))+
  geom_treemap(fill=brewer.pal(6, "Blues")[4:6], color=1, alpha=.8)+
  geom_treemap_text(colour = "black", place = "centre", grow = FALSE, size=10)+
  ggtitle("Apportioned Variance")+
  theme(plot.background = element_blank())+
  theme(plot.title = element_text(hjust = 0.5))

q0.plot
```


#####Constrained Analysis of Principle Components
<br />


```{r}
#Constrained Analysis of Principle Components
cap_ord <- ordinate(
  physeq = physeq_obj.occ_fish, 
  method = "CAP",
  distance = d_carn,
  formula = ~ Site+Location
)
#Results of model
anova(cap_ord)
```

```{r, results="hide",warning=FALSE}
# CAP plot of environmental predictor variables
sample_data(physeq_obj.occ_fish)$Location = factor(sample_data(physeq_obj.occ_fish)$Location, levels = c("Edge_A", "Edge_B", "Edge_C","MPA_A", "MPA_B", "MPA_C","Outside_A","Outside_B","Outside_C"))
get_variable(physeq_obj.occ_fish, "Location")

cap_plot <- plot_ordination(
  physeq = physeq_obj.occ_fish, 
  ordination = cap_ord, 
  color = "Location", 
  axes = c(1,2)
) + 
  aes(shape = Site) + 
  geom_point(aes(colour = Location), size = 4) + 
  geom_point(colour = "grey90", size = 1.5) + 
  scale_color_manual(values = c(col.great4)
  )

# Now add the environmental variables as arrows
arrowmat <- vegan::scores(cap_ord, display = "bp")

# Add labels, make a data.frame
arrowdf <- data.frame(labels = rownames(arrowmat), arrowmat)
arrowdf %>% filter(., labels=="SiteMPA") ->arrowdf
arrowdf$labels <- c("MPA")

# Define the arrow aesthetic mapping
arrow_map <- aes(xend = CAP1, 
                 yend = CAP2, 
                 x = 0, 
                 y = 0, 
                 shape = NULL, 
                 color = NULL, 
                 label = labels)

label_map <- aes(x = 0.92 * CAP1, 
                 y = 1.3 * CAP2, 
                 shape = NULL, 
                 color = NULL, 
                 label = labels)

arrowhead = arrow(length = unit(0.02, "npc"))

#Hulls for each polygon

test <- vegan::scores(cap_ord, display = "sites")

data.scores_1 <- as.data.frame(scores(test))  
#Using the scores function from vegan to extract the site scores and 
# convert to a data.frame
data.scores_1$Site <- sampledf$Site  
# create a column of site names, from the rownames of data.scores

#Add location data
grp <- sampledf$Location
data.scores_1$grp <- grp  #  add the grp variable created earlier

#### Calculate Shape Around Points
grp.Edge_A <- data.scores_1[data.scores_1$grp == "Edge_A", ][chull(data.scores_1[data.scores_1$grp == "Edge_A", c("CAP1", "CAP2")]), ]  
grp.Edge_B <- data.scores_1[data.scores_1$grp == "Edge_B", ][chull(data.scores_1[data.scores_1$grp == "Edge_B", c("CAP1", "CAP2")]), ]
grp.Edge_C <- data.scores_1[data.scores_1$grp == "Edge_C", ][chull(data.scores_1[data.scores_1$grp == "Edge_C", c("CAP1", "CAP2")]), ]
grp.Outside_A <- data.scores_1[data.scores_1$grp == "Outside_A", ][chull(data.scores_1[data.scores_1$grp == "Outside_A", c("CAP1", "CAP2")]), ]  
grp.Outside_B <- data.scores_1[data.scores_1$grp == "Outside_B", ][chull(data.scores_1[data.scores_1$grp == "Outside_B", c("CAP1", "CAP2")]), ]
grp.Outside_C <- data.scores_1[data.scores_1$grp == "Outside_C", ][chull(data.scores_1[data.scores_1$grp == "Outside_C", c("CAP1", "CAP2")]), ]
grp.MPA_A <- data.scores_1[data.scores_1$grp == "MPA_A", ][chull(data.scores_1[data.scores_1$grp == "MPA_A", c("CAP1", "CAP2")]), ]  
grp.MPA_B <- data.scores_1[data.scores_1$grp == "MPA_B", ][chull(data.scores_1[data.scores_1$grp == "MPA_B", c("CAP1", "CAP2")]), ]
grp.MPA_C <- data.scores_1[data.scores_1$grp == "MPA_C", ][chull(data.scores_1[data.scores_1$grp == "MPA_C", c("CAP1", "CAP2")]), ]

hull.data <- rbind(grp.Edge_A, grp.Edge_B,grp.Edge_C,grp.Outside_A,grp.Outside_B,grp.Outside_C,grp.MPA_A,grp.MPA_B,grp.MPA_C)
colnames(hull.data)[4] <- c("Location")

# Make a new graphic for the constrained ordination

cap_1 <- cap_plot +  
  theme_bw(base_size = 18)+
  geom_segment(
    mapping = arrow_map, 
    size = .5, 
    data = arrowdf, 
    color = "grey", 
    arrow = arrowhead
  ) +
  geom_text(
    mapping = label_map, 
    size = 6,  
    data = arrowdf, 
    show.legend = FALSE
  ) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(),  panel.border = element_rect(colour = "black", fill=NA, size=2))+
  scale_fill_manual(name  ="Location",
                            breaks=c("Edge_A", "Edge_B", "Edge_C","MPA_A", "MPA_B", "MPA_C","Outside_A","Outside_B","Outside_C"),
                            labels=c("Edge_A", "Edge_B", "Edge_C","MPA_A", "MPA_B", "MPA_C","Outside_A","Outside_B","Outside_C"), 
                        values = c(col.great4))+
  geom_polygon(data=hull.data,aes(x=CAP1,y=CAP2,fill=grp, group=grp),alpha=0.30) + 
  scale_fill_manual(name  ="Location",
                            breaks=c("Edge_A", "Edge_B", "Edge_C","MPA_A", "MPA_B", "MPA_C","Outside_A","Outside_B","Outside_C"),
                             labels=c("Edge_A", "Edge_B", "Edge_C","MPA_A", "MPA_B", "MPA_C","Outside_A","Outside_B","Outside_C"),
                        values = c(col.great4)) +
    ggtitle("Constrained Analysis of Principle Components")

cap_1

```

```{r}
ggsave(filename = "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/figures/CAP.eps",
       plot = plot(cap_1),
       device = cairo_ps,
       dpi = 300,
       width = 12,
  height = 8,
  units = c("in"))
```


##### CAP ordinate
<br />

```{r, results="hide",warning=FALSE}
#Run CAP analysis to identify predictor species
vare.cap <- capscale(carnivore_rel_abun ~ Site + Location, data=sampledf, dist="bray")

#Retain species scores
sppscores(vare.cap) <- carnivore_rel_abun

as.data.frame(vegan::scores(vare.cap, display="species")) %>% 
  rownames_to_column(var = "sample") %>% 
  as.tibble %>%
 mutate(dist = sqrt((CAP1 - 0)^2 + (CAP2 - 0)^2)) -> vare.cap_species_distances

vare.cap_species_distances %>% arrange(dist) %>% ggplot(., aes(y=dist, x=reorder(sample,-dist))) +geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))


ggplot(data=vare.cap_species_distances, aes(vare.cap_species_distances$dist)) + geom_histogram()
  
vare.cap_species_distances %>% 
  top_n(7, dist) -> top_species
top_species <- as.data.frame(top_species)
rownames(top_species) <- top_species$sample

# Now add the environmental variables as arrows
arrowmat <- top_species

#Rename row names to clean up plot

rownames(top_species) %>% as.data.frame() -> namers
colnames(namers) <- c("path")
namers %>% separate(path, c("P","C","O","F","G","Species"), sep=";") %>% 
mutate(., name = ifelse(Species == "", G, Species)) -> namers

rownames(arrowmat) <- namers$name

# Add labels, make a data.frame
arrowdf <- data.frame(labels = rownames(arrowmat), arrowmat)

# Define the arrow aesthetic mapping
arrow_map <- aes(xend = CAP1, 
                 yend = CAP2, 
                 x = 0, 
                 y = 0, 
                 shape = NULL, 
                 color = NULL, 
                 label = labels)

label_map <- aes(x = 0.75 * CAP1, 
                 y = 0.75 * CAP2, 
                 shape = NULL, 
                 color = NULL, 
                 label = labels)

arrowhead = arrow(length = unit(0.02, "npc"))

#Hulls for each polygon

test.2 <- as.data.frame(vare.cap$CCA$wa)

data.scores_1 <- as.data.frame(scores(test.2))  
#Using the scores function from vegan to extract the site scores and 
# convert to a data.frame
data.scores_1$Site <- sampledf$Site  
# create a column of site names, from the rownames of data.scores
head(data.scores_1) 

grp <- sampledf$Location
data.scores_1$grp <- grp  #  add the grp variable created earlier

#Add location data
grp <- sampledf$Location
data.scores_1$grp <- grp  #  add the grp variable created earlier

#### Calculate Shape Around Points
grp.Edge_A <- data.scores_1[data.scores_1$grp == "Edge_A", ][chull(data.scores_1[data.scores_1$grp == "Edge_A", c("CAP1", "CAP2")]), ]  
grp.Edge_B <- data.scores_1[data.scores_1$grp == "Edge_B", ][chull(data.scores_1[data.scores_1$grp == "Edge_B", c("CAP1", "CAP2")]), ]
grp.Edge_C <- data.scores_1[data.scores_1$grp == "Edge_C", ][chull(data.scores_1[data.scores_1$grp == "Edge_C", c("CAP1", "CAP2")]), ]
grp.Outside_A <- data.scores_1[data.scores_1$grp == "Outside_A", ][chull(data.scores_1[data.scores_1$grp == "Outside_A", c("CAP1", "CAP2")]), ]  
grp.Outside_B <- data.scores_1[data.scores_1$grp == "Outside_B", ][chull(data.scores_1[data.scores_1$grp == "Outside_B", c("CAP1", "CAP2")]), ]
grp.Outside_C <- data.scores_1[data.scores_1$grp == "Outside_C", ][chull(data.scores_1[data.scores_1$grp == "Outside_C", c("CAP1", "CAP2")]), ]
grp.MPA_A <- data.scores_1[data.scores_1$grp == "MPA_A", ][chull(data.scores_1[data.scores_1$grp == "MPA_A", c("CAP1", "CAP2")]), ]  
grp.MPA_B <- data.scores_1[data.scores_1$grp == "MPA_B", ][chull(data.scores_1[data.scores_1$grp == "MPA_B", c("CAP1", "CAP2")]), ]
grp.MPA_C <- data.scores_1[data.scores_1$grp == "MPA_C", ][chull(data.scores_1[data.scores_1$grp == "MPA_C", c("CAP1", "CAP2")]), ]

hull.data <- rbind(grp.Edge_A, grp.Edge_B,grp.Edge_C,grp.Outside_A,grp.Outside_B,grp.Outside_C,grp.MPA_A,grp.MPA_B,grp.MPA_C)
colnames(hull.data)[4] <- c("Location")


# Plot CAP
as.data.frame(vare.cap$CCA$wa) %>% 
  rownames_to_column(var = "sample") %>% 
  as.tibble() %>% 
  separate(sample, into = c("Site","Location", "rep") , sep = "\\.", remove = F) %>%
  mutate(Site1=Site) %>% 
  unite(Site, Location, col= "Location", remove=F) %>% 
  mutate(Location=dplyr::recode(Location, "LSC_A"="Edge_A",
                    "LSC_B"= "Edge_B",
                    "LSC_C"="Edge_C",
                    "PedRF_A"="Outside_A",
                    "PedRF_B"="Outside_B",
                    "PedRF_C"="Outside_C",
                    "PP_A"="MPA_A",
                    "PP_B"="MPA_B",
                    "PP_C"="MPA_C")) %>% 
   mutate(Site=dplyr::recode(Site, "LSC"="Edge","PedRF"="Outside","PP"="MPA")) -> data_cap

cap_species <-  data_cap %>% 
  ggplot(aes(x=CAP1, y=CAP2)) + geom_point(aes(col=Location, shape=Site), size =3) + scale_color_manual(values = c(col.great3), labels=c("Edge_A", "Edge_B", "Edge_C","MPA_A", "MPA_B", "MPA_C","Outside_A","Outside_B","Outside_C")) + geom_segment(
    mapping = arrow_map, 
    size = .5, 
    data = arrowdf, 
    color = "grey", 
    arrow = arrowhead
  ) +
  geom_text(
    mapping = label_map, 
    size = 5,  
    data = arrowdf, 
    show.legend = FALSE,
    position=position_jitter(width=0.05,height=0.08)
  ) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(),  panel.border = element_rect(colour = "black", fill=NA, size=2))+
  scale_fill_manual(name  ="Location",
                            labels=c("Edge_A", "Edge_B", "Edge_C","MPA_A", "MPA_B", "MPA_C","Outside_A","Outside_B","Outside_C"),
                            breaks=c("Edge_A", "Edge_B", "Edge_C","MPA_A", "MPA_B", "MPA_C","Outside_A","Outside_B","Outside_C"), 
                        values = c(col.great3))+
  geom_polygon(data=hull.data,aes(x=CAP1,y=CAP2,fill=grp, group=grp),alpha=0.30) + 
  scale_fill_manual(name  ="Location",
                            breaks=c("Edge_A", "Edge_B", "Edge_C","MPA_A", "MPA_B", "MPA_C","Outside_A","Outside_B","Outside_C"),
                            labels=c("Edge_A", "Edge_B", "Edge_C","MPA_A", "MPA_B", "MPA_C","Outside_A","Outside_B","Outside_C"), 
                        values = c(col.great3)) + ylab("CAP2 [9.2%]")   + xlab("CAP1 [12.6%]") +theme(plot.title = element_text(hjust = 0.5,size = 30, face = "bold"),
        axis.text=element_text(size=20),
        axis.title=element_text(size=24,face="bold"),
        legend.title=element_text(size=20),
        legend.text=element_text(size=18),
        plot.subtitle = element_text(size=20),
        legend.spacing.y = unit(0.5, 'cm'), 
        legend.key = element_rect(size = 10),
        legend.key.size = unit(2, 'lines'))

cap_species
```
```{r}
ggsave(filename = "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/figures/CAP_species.eps",
       plot = plot(cap_species),
       device = cairo_ps,
       dpi = 300,
       width = 12,
  height = 8,
  units = c("in"))
```

```{r}
species_distances <- as.data.frame(vare.cap_species_distances)
rownames(species_distances) <- species_distances$sample

# Now add the environmental variables as arrows
arrowmat <- species_distances

#Rename row names to clean up plot

rownames(species_distances) %>% as.data.frame() -> namers
colnames(namers) <- c("path")
namers %>% separate(path, c("D1","P1","C1","O1","F1","G1","Species"), sep=";") %>% replace(is.na(.), "") %>% 
  mutate(O1=recode(O1, `NA`=="")) %>% 
mutate(., name = ifelse(Species == "", G1, Species)) %>% 
  mutate(., name = ifelse(name == "", F1, name)) %>% 
  mutate(., name = ifelse(name == "", O1, name)) %>% 
  mutate(., name = ifelse(name == "", C1, name)) %>% 
  mutate(., name = ifelse(name == "", P1, name))-> namers

rownames(arrowmat) <- namers$name

# Add labels, make a data.frame
arrowdf <- data.frame(labels = rownames(arrowmat), arrowmat)

arrowdf %>% 
arrange(desc(dist)) %>% 
ggplot(., aes(x= reorder(labels, -dist), y=dist)) +
  geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

##### NMDS Plots
<br />

```{r, results="hide",warning=FALSE}
# NMDS ordination
ord <- ordinate(physeq_obj.occ_fish, method = "NMDS", distance = d_carn)
ord

nmdsplot <- plot_ordination(physeq_obj.occ, ord, color = "Site", shape="Site") +
  geom_point(size=10) +
  theme_bw() +
  #geom_text(aes(x=NMDS1,y=NMDS2,label=Replicate),alpha=0.5)+
   ggtitle(paste("NMDS Bray-Curtis Dissimilarity Method"))  + stat_ellipse(geom = "path", type="norm", aes(group=Site, color=Site),linetype = 2)  + scale_color_manual(values=c(col_mpa[2],col_mpa[1],col_mpa[3]))+
 theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.text=element_text(size=16),
        axis.title=element_text(size=20,face="bold"),legend.title = element_text( size=12, face="bold"),legend.text = element_text(size=10, face="bold"))

nmdsplot
```

```{r}
ggsave(filename = "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/figures/nmds_site.eps",
       plot = plot(nmdsplot),
       device = cairo_ps,
       dpi = 300,
       width = 12,
  height = 8,
  units = c("in"))
```

```{r, results="hide",warning=FALSE}
# NMDS ordination
ord <- ordinate(physeq_obj.occ_fish, method = "NMDS", distance = d_carn)
ord

sample_data(physeq_obj.occ)

nmdsplot <- plot_ordination(physeq_obj.occ, ord, color = "Site", shape="Rep") +
  geom_point(size=10) +
  theme_bw() + stat_ellipse(geom = "path", type="norm", aes(group=Site, color=Site),linetype = 2) + scale_color_manual(values=c(col_mpa[2],col_mpa[1],col_mpa[3]))+
 theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.text=element_text(size=16),
        axis.title=element_text(size=20,face="bold"),legend.title = element_text( size=12, face="bold"),legend.text = element_text(size=10, face="bold")) + labs(shape = "Location")

nmdsplot
```

```{r}
ggsave(filename = "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/figures/nmds_location.eps",
       plot = plot(nmdsplot),
       device = cairo_ps,
       dpi = 300,
       width = 12,
  height = 8,
  units = c("in"))
```



```{r, results="hide",warning=FALSE}
# NMDS ordination
ord <- ordinate(physeq_obj.step2, method = "NMDS", distance = d_carn_2)

nmdsplot <- plot_ordination(physeq_obj.step2, ord, color = "Location", shape="Site") +
  geom_point(size=5) +
  theme_bw() +
  #geom_text(aes(x=NMDS1,y=NMDS2,label=Replicate),alpha=0.5)+
   ggtitle(paste("NMDS Bray-Curtis Dissimilarity Method")) +
  scale_color_manual(values=col.great) + scale_fill_manual(values=col.great)
nmdsplot + stat_ellipse(geom = "polygon", type="norm", alpha=0.1, aes(group=Site, fill=Site))  + scale_fill_manual(values=c("#00A08A","#FF0000","#F2AD00"))

#no convergence with NMDS, suggests that no difference between sites when not running occupancy modeling
```



```{r, results="hide",warning=FALSE}
# NMDS ordination
ord <- ordinate(physeq_obj.occ_fish, method = "NMDS", distance = d_carn_j)
ord

nmdsplot <- plot_ordination(physeq_obj.occ, ord, color = "Site", shape="Site") +
  geom_point(size=10) +
  theme_bw() +
  #geom_text(aes(x=NMDS1,y=NMDS2,label=Replicate),alpha=0.5)+
   ggtitle(paste("NMDS Jaccard Dissimilarity Method"))  + stat_ellipse(geom = "path", type="norm", aes(group=Site, color=Site),linetype = 2)  + scale_color_manual(values=c(col_mpa[2],col_mpa[1],col_mpa[3]))+
 theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.text=element_text(size=16),
        axis.title=element_text(size=20,face="bold"),legend.title = element_text( size=12, face="bold"),legend.text = element_text(size=10, face="bold"))

nmdsplot
```
##### Gradient Forest
<br />
<br />


```{r, results="hide",warning=FALSE}
#Remake Indexed OTU table
carn_ra_num <- as.data.frame(carnivore_rel_abun)

#Make Numeric
carn_ra_num <- as.data.frame(carnivore_rel_abun)
carn_ra_num <- sapply(carn_ra_num, as.numeric)

#Re apply row and col names
row.names(carn_ra_num) <- row.names(carnivore_rel_abun)
colnames(carn_ra_num) <- colnames(carnivore_rel_abun)

#Rename Column Names
species_names <- colnames(carnivore_rel_abun)
easy_name <- vector(length=length(species_names))

for (i in 1:length(easy_name)) {
  easy_name[i] <- paste0("species", i)
}
#colnames(carn_ra_num) <- easy_name

#Store Name Pairs
species_list <- as.list(easy_name,species_names)
names(species_names) <- easy_name

#sites are rows (same order as metadata)
#species are columns

##########################
# COMBINE BOTH DATA SETS #
##########################
input_meta_path2 <- "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/mpa_metadata_gradfor.txt"
metadata2 <- read.table(input_meta_path2, header = 1, sep = "\t", stringsAsFactors = F)
metadata2 <- as.data.frame(metadata2)
row_namers <- metadata2$Samples
metadata2 <- sapply(metadata2, as.numeric)
row.names(metadata2) <- row_namers
metadata2 <- metadata2[,2:4]

datDF_carn<-merge(metadata2,carn_ra_num,by="row.names")
g <- length(datDF_carn)
row_namers2 <- row.names(carn_ra_num)
datDF_carn <- sapply(datDF_carn, as.numeric)
datDF_carn <- datDF_carn[,2:g]
datDF_carn <- as.data.frame(datDF_carn)
row.names(datDF_carn) <- row_namers2 

###########################
# GRADIENT FOREST EXAMPLE #
###########################

eDNA_gradFor<-gradientForest(datDF_carn,
                             predictor.vars = colnames(metadata2), 
                             response.vars = colnames(carn_ra_num),
                             ntree = 5000, transform = NULL, compact = F,
                             corr.threshold = 0.5, trace=T)
```

```{r}
#Plot Overall Importance of Environmental Variables
plot(eDNA_gradFor,plot.type="Overall.Importance", col=col_grad, cex.axis=1.5, cex.main=2)
```

<br />

***Figure 18.** Overall Importance of Environmental Variables from Gradient Forest Analysis* 
<br />
<br />


```{r}
#R^2 fit for each species
plot(eDNA_gradFor, plot.type = "Performance", show.names = F, horizontal = F,
     cex.axis = 1, cex.labels = 0.7, line = 2.5)

```

```{r}
most_important <- names(importance(eDNA_gradFor))
par(mgp = c(2, 0.75, 0))

plot(eDNA_gradFor, plot.type = "S", imp.vars = most_important,
 leg.posn = "top", cex.legend = 1.5, cex.axis = 2.5,
 cex.lab = 2, line.ylab = 2.5, par.args = list(mgp = c(5,
 3, 1), mar=c(6,4,0,0)))
```


```{r}
sort(eDNA_gradFor$result, decreasing=T)
```

#Plot Top Species
```{r}
goodTaxa = names(sort(eDNA_gradFor$result, decreasing=T))
goodTaxa = goodTaxa[1]
badTaxa <- setdiff(taxa_names(physeq_obj.occ), goodTaxa)
top_hits <- prune_taxa(goodTaxa, physeq_obj.occ)

# convert your processed phyloseq object into a dataframe
df <- psmelt(top_hits)

# group by Treatment and Family, calculate mean abundance and standard deviation
avgs <- df %>% group_by(Site,Species) %>% 
  summarise(mean = mean(Abundance),
  sd = sd(Abundance))

# plot bar graph with standard deviation as error bars
p<-ggplot(avgs, aes(x=Site, y=mean)) + 
    geom_bar(aes(fill=Site), stat="identity") + scale_fill_manual(values=col_mpa4)+
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd),
                  width=0.2,
                  size=0.5) + 
  ggtitle(label =paste0(avgs$Species[1])) +theme_bw() + 
  theme(legend.position="none", panel.grid.minor.y=element_blank(),panel.grid.minor.x=element_blank(),panel.grid.major.y=element_blank(),panel.grid.major.x=element_blank()) +ylab("eDNA Index")

neworder = c("MPA", "Edge", "Outside")

p$data$Site <- as.character(p$data$Site)
p$data$Site <- factor(p$data$Site, levels=neworder)
p


```

```{r}
goodTaxa = names(sort(eDNA_gradFor$result, decreasing=T))
goodTaxa = goodTaxa
badTaxa <- setdiff(taxa_names(physeq_obj.occ), goodTaxa)
top_hits <- prune_taxa(goodTaxa, physeq_obj.occ)

# convert your processed phyloseq object into a dataframe
df <- psmelt(top_hits)
df$Species <- as.character(df$Species)
df$Genus <- as.character(df$Genus)
df$Family <- as.character(df$Family)
df$Order <- as.character(df$Order)
df$Class <- as.character(df$Class)
df$Phylum <- as.character(df$Phylum)
colnames(df)
class(df)
df %>%
  mutate(., name = ifelse(Species == "", Genus, Species)) %>% 
  mutate(., name = ifelse(name == "", Family, name)) %>% 
  mutate(., name = ifelse(name == "", Order, name)) %>% 
  mutate(., name = ifelse(name == "", Class, name)) %>% 
  mutate(., name = ifelse(name == "", Phylum, name))-> df2
df2$name
# group by Treatment and Family, calculate mean abundance and standard deviation
avgs <- df2 %>% group_by(Site,name) %>% 
  summarise(mean = mean(Abundance),
  sd = sd(Abundance))

avgs$Site <- factor(avgs$Site,levels = c("MPA", "Edge", "Outside"))

# plot bar graph with standard deviation as error bars

avgs %>%
  dplyr::group_by(name) %>% 
  nest()%>% 
  mutate(plot = map2(data,name, ~ggplot(.x, aes(x=Site, y=mean)) + 
    geom_bar(aes(fill=Site), stat="identity") + scale_fill_manual(values=col_mpa4)+
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd),
                  width=0.2,
                  size=0.5) + 
  ggtitle(as.character(.y)) +theme_bw() + 
  theme(legend.position="none", panel.grid.minor.y=element_blank(),panel.grid.minor.x=element_blank(),panel.grid.major.y=element_blank(),panel.grid.major.x=element_blank()) +ylab("eDNA Index")))-> grad_for_top_abund

multiplot(grad_for_top_abund$plot[[1]],
          grad_for_top_abund$plot[[2]],
          grad_for_top_abund$plot[[3]],
          grad_for_top_abund$plot[[4]],
          grad_for_top_abund$plot[[5]],
          grad_for_top_abund$plot[[6]],
          grad_for_top_abund$plot[[7]],
          grad_for_top_abund$plot[[8]], 
          grad_for_top_abund$plot[[9]], 
          grad_for_top_abund$plot[[10]],
          grad_for_top_abund$plot[[11]],
          grad_for_top_abund$plot[[12]],
          grad_for_top_abund$plot[[13]],
          grad_for_top_abund$plot[[14]],
          grad_for_top_abund$plot[[15]],
          grad_for_top_abund$plot[[16]],
          grad_for_top_abund$plot[[17]],
          grad_for_top_abund$plot[[18]],
          grad_for_top_abund$plot[[19]],cols=4)

```
```{r}
ggsave(filename = "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/figures/gradfor_top_species.eps",
       plot = multiplot(grad_for_top_abund$plot[[1]],
          grad_for_top_abund$plot[[2]],
          grad_for_top_abund$plot[[3]],
          grad_for_top_abund$plot[[4]],
          grad_for_top_abund$plot[[5]],
          grad_for_top_abund$plot[[6]],
          grad_for_top_abund$plot[[7]],
          grad_for_top_abund$plot[[8]], 
          grad_for_top_abund$plot[[9]], 
          grad_for_top_abund$plot[[10]],
          grad_for_top_abund$plot[[11]],
          grad_for_top_abund$plot[[12]],
          grad_for_top_abund$plot[[13]],
          grad_for_top_abund$plot[[14]],
          grad_for_top_abund$plot[[15]],
          grad_for_top_abund$plot[[16]],
          grad_for_top_abund$plot[[17]],
          grad_for_top_abund$plot[[18]],
          grad_for_top_abund$plot[[19]],cols=4),
       device = cairo_ps,
       dpi = 300,
       width = 12,
  height = 12,
  units = c("in"))
```

```{r}

species_distances <- as.data.frame(vare.cap_species_distances)
rownames(species_distances) <- species_distances$sample

# Now add the environmental variables as arrows
arrowmat <- species_distances

#Rename row names to clean up plot

rownames(species_distances) %>% as.data.frame() -> namers
colnames(namers) <- c("path")
namers %>% separate(path, c("D1","P1","C1","O1","F1","G1","Species"), sep=";") %>% replace(is.na(.), "") %>% 
  mutate(O1=recode(O1, `NA`="")) %>% 
mutate(., name = ifelse(Species == "", G1, Species)) %>% 
  mutate(., name = ifelse(name == "", F1, name)) %>% 
  mutate(., name = ifelse(name == "", O1, name)) %>% 
  mutate(., name = ifelse(name == "", C1, name)) %>% 
  mutate(., name = ifelse(name == "", P1, name))-> namers

rownames(arrowmat) <- namers$name

# Add labels, make a data.frame
arrowdf <- data.frame(labels = rownames(arrowmat), arrowmat)

arrowdf %>% arrange(desc(dist)) %>%
  top_n(20, dist) %>% dplyr::select(sample) -> top_species_cap

goodTaxa = top_species_cap$sample
goodTaxa = goodTaxa
badTaxa <- setdiff(taxa_names(physeq_obj.occ), goodTaxa)
top_hits <- prune_taxa(goodTaxa, physeq_obj.occ)

# convert your processed phyloseq object into a dataframe
df <- psmelt(top_hits)
df$Species <- as.character(df$Species)
df$Genus <- as.character(df$Genus)
df$Family <- as.character(df$Family)
df$Order <- as.character(df$Order)
df$Class <- as.character(df$Class)
df$Phylum <- as.character(df$Phylum)
colnames(df)
class(df)
df %>%
  mutate(., name = ifelse(Species == "", Genus, Species)) %>% 
  mutate(., name = ifelse(name == "", Family, name)) %>% 
  mutate(., name = ifelse(name == "", Order, name)) %>% 
  mutate(., name = ifelse(name == "", Class, name)) %>% 
  mutate(., name = ifelse(name == "", Phylum, name))-> df2
df2$name
# group by Treatment and Family, calculate mean abundance and standard deviation
avgs <- df2 %>% group_by(Site,name) %>% 
  summarise(mean = mean(Abundance),
  sd = sd(Abundance))

avgs$Site <- factor(avgs$Site,levels = c("MPA", "Edge", "Outside"))

# plot bar graph with standard deviation as error bars

avgs %>%
  dplyr::group_by(name) %>% 
  nest()%>% 
  mutate(plot = map2(data,name, ~ggplot(.x, aes(x=Site, y=mean)) + 
    geom_bar(aes(fill=Site), stat="identity") + scale_fill_manual(values=col_mpa4)+
    geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd),
                  width=0.2,
                  size=0.5) + 
  ggtitle(as.character(.y)) +theme_bw() + 
  theme(legend.position="none", panel.grid.minor.y=element_blank(),panel.grid.minor.x=element_blank(),panel.grid.major.y=element_blank(),panel.grid.major.x=element_blank()) +ylab("eDNA Index")))-> grad_for_top_abund

multiplot(grad_for_top_abund$plot[[1]],
          grad_for_top_abund$plot[[2]],
          grad_for_top_abund$plot[[3]],
          grad_for_top_abund$plot[[4]],
          grad_for_top_abund$plot[[5]],
          grad_for_top_abund$plot[[6]],
          grad_for_top_abund$plot[[7]],
          grad_for_top_abund$plot[[8]], 
          grad_for_top_abund$plot[[9]], 
          grad_for_top_abund$plot[[10]],
          grad_for_top_abund$plot[[11]],
          grad_for_top_abund$plot[[12]],
          grad_for_top_abund$plot[[13]],
          grad_for_top_abund$plot[[14]],
          grad_for_top_abund$plot[[15]],
          grad_for_top_abund$plot[[16]],
          grad_for_top_abund$plot[[17]],
          grad_for_top_abund$plot[[18]],
          grad_for_top_abund$plot[[19]],
          grad_for_top_abund$plot[[20]],cols=4)
```

```{r}
ggsave(filename = "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/figures/CAP_species.eps",
       plot = multiplot(grad_for_top_abund$plot[[1]],
          grad_for_top_abund$plot[[2]],
          grad_for_top_abund$plot[[3]],
          grad_for_top_abund$plot[[4]],
          grad_for_top_abund$plot[[5]],
          grad_for_top_abund$plot[[6]],
          grad_for_top_abund$plot[[7]],
          grad_for_top_abund$plot[[8]], 
          grad_for_top_abund$plot[[9]], 
          grad_for_top_abund$plot[[10]],
          grad_for_top_abund$plot[[11]],
          grad_for_top_abund$plot[[12]],
          grad_for_top_abund$plot[[13]],
          grad_for_top_abund$plot[[14]],
          grad_for_top_abund$plot[[15]],
          grad_for_top_abund$plot[[16]],
          grad_for_top_abund$plot[[17]],
          grad_for_top_abund$plot[[18]],
          grad_for_top_abund$plot[[19]],
          grad_for_top_abund$plot[[20]],cols=4),
       device = cairo_ps,
       dpi = 300,
       width = 12,
  height = 12,
  units = c("in"))
```

#NPS Data
```{r}

nps_sites_path <- "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/jan_2020_analysis/analysis_2/nps_species_sites_02032020.csv"
nps_sites <- read.table(nps_sites_path, header = 1, sep = ",", stringsAsFactors = F)
nps_sites <- as.data.frame(nps_sites)



ped_nps <- nps_sites$PedRF_species
lsc_nps <- nps_sites$LSC_species
pp_nps <- nps_sites$PP_species

append(append(ped_nps,lsc_nps),pp_nps) %>% unique() -> nps_all_unique

ped_nps_df <- as.data.frame(ped_nps)
lsc_nps_df <- as.data.frame(lsc_nps)
pp_nps_df <- as.data.frame(pp_nps)

names(ped_nps_df) <- "Species"
names(lsc_nps_df) <- "Species"
names(pp_nps_df) <- "Species"

lsc_nps_df %>% 
filter(., Species !="") -> lsc_nps_df
ped_nps_df %>% 
filter(., Species !="") -> ped_nps_df
pp_nps_df %>% 
filter(., Species !="") -> pp_nps_df

intersect(intersect(ped_nps_df$Species,lsc_nps_df$Species), pp_nps_df$Species) -> common_species_nps

setdiff(ped_nps_df$Species,union(pp_nps_df$Species, lsc_nps_df$Species)) -> outside_species_unique_nps
setdiff(lsc_nps_df$Species,union(pp_nps_df$Species, ped_nps_df$Species)) -> edge_species_unique_nps
setdiff(pp_nps_df$Species,union(ped_nps_df$Species, lsc_nps_df$Species)) -> mpa_species_unique_nps

setdiff(intersect(ped_nps_df$Species, lsc_nps_df$Species),pp_nps_df$Species) -> outside_edge_species_common_nps
setdiff(intersect(ped_nps_df$Species, pp_nps_df$Species),lsc_nps_df$Species) -> outside_mpa_species_common_nps
setdiff(intersect(pp_nps_df$Species, lsc_nps_df$Species),ped_nps_df$Species) -> edge_mpa_species_common_nps

grid.newpage()
nps_venn_plot <- draw.triple.venn(area1 = length(ped_nps_df$Species),
                 area2 = length(lsc_nps_df$Species),
                 area3 = length(pp_nps_df$Species),
                 n12 = (length(outside_edge_species_common_nps)+length(common_species_nps)),
                 n23 = (length(edge_mpa_species_common_nps)+length(common_species_nps)),
                 n13 = (length(outside_mpa_species_common_nps)+length(common_species_nps)),
                 n123 = length(common_species_nps),
                 lwd = rep(1, 3),
                 lty =rep("solid", 3), 
                 col = rep("black", 3),
                 cex= rep(2, 7),
                 cat.pos = c(-40, 40, 180),
                 cat.dist =c(0.08, 0.08, 0.08),
                 fontface = rep("plain", 7),
                 fontfamily = rep("sans", 7),
                 cat.cex = rep(2, 3),
                 cat.fontface = rep("plain", 3),
                 cat.fontfamily = rep("sans", 3),
                 category = c("Outside", "Edge", "MPA"),  
                 fill = c(col_mpa[3],col_mpa[2],col_mpa[1]),
                 alpha = 0.8)




```


```{r}
ggsave(filename = "/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/figures/nps_venn_plot.eps",
       plot = grid.draw(nps_venn_plot),
       device = cairo_ps,
       dpi = 300,
       width = 10,
  height = 8,
  units = c("in"))
```

```{r}
setdiff(nps_all_unique,get_taxa_unique(physeq_obj.occ,"Species"))
setdiff(nps_all_unique,get_taxa_unique(physeq_obj.step2,"Species"))
intersect(nps_all_unique,get_taxa_unique(physeq_obj.step2,"Species"))
nps_all_unique

```

```{r}

outside <- physeq_obj.step2_fish %>% subset_samples(Site == "Outside")
edge <- physeq_obj.step2_fish %>% subset_samples(Site == "Edge")
mpa <- physeq_obj.step2_fish %>% subset_samples(Site == "MPA")

outside <- prune_taxa(
  taxa = apply(otu_table(outside), 1, function(x){sum(x>0) >= 1}), 
  x = outside)

edge <- prune_taxa(
  taxa = apply(otu_table(edge), 1, function(x){sum(x>0) >= 1}), 
  x = edge)

mpa <- prune_taxa(
  taxa = apply(otu_table(mpa), 1, function(x){sum(x>0) >= 1}), 
  x = mpa)

outside_species <- taxa_names(outside)
edge_species <- taxa_names(edge)
mpa_species <- taxa_names(mpa)

outside_species_df <- as.data.frame(outside_species)
edge_species_df <- as.data.frame(edge_species)
mpa_species_df <- as.data.frame(mpa_species)

names(outside_species_df) <- "Species"
names(edge_species_df) <- "Species"
names(mpa_species_df) <- "Species"


intersect(intersect(outside_species_df$Species,edge_species_df$Species), mpa_species_df$Species) -> common_species

setdiff(outside_species_df$Species,union(mpa_species_df$Species, edge_species_df$Species)) -> outside_species_unique
setdiff(edge_species_df$Species,union(mpa_species_df$Species, outside_species_df$Species)) -> edge_species_unique
setdiff(mpa_species_df$Species,union(outside_species_df$Species, edge_species_df$Species)) -> mpa_species_unique

setdiff(intersect(outside_species_df$Species, edge_species_df$Species),mpa_species_df$Species) -> outside_edge_species_common
setdiff(intersect(outside_species_df$Species, mpa_species_df$Species),edge_species_df$Species) -> outside_mpa_species_common
setdiff(intersect(mpa_species_df$Species, edge_species_df$Species),outside_species_df$Species) -> edge_mpa_species_common

```

```{r}
common_species %>% as.data.frame() %>% 
separate(., ., into = c("Domain","Phylum","Class","Order","Family","Genus","Species"), sep=";") %>% dplyr::select(Species) -> common_species_mpa

mpa_species_df %>% as.data.frame() %>% 
separate(., Species, into = c("Domain","Phylum","Class","Order","Family","Genus","Species"), sep=";") %>% dplyr::select(Species) -> eDNA_mpa_species_all

mpa_species_unique %>% as.data.frame() %>% 
separate(., ., into = c("Domain","Phylum","Class","Order","Family","Genus","Species"), sep=";") %>% dplyr::select(Species) -> eDNA_mpa_species_unique

outside_species_df %>% as.data.frame() %>% 
separate(., Species, into = c("Domain","Phylum","Class","Order","Family","Genus","Species"), sep=";") %>% dplyr::select(Species) -> eDNA_outside_species_df

edge_species_df %>% as.data.frame() %>% 
separate(., Species, into = c("Domain","Phylum","Class","Order","Family","Genus","Species"), sep=";") %>% dplyr::select(Species) -> eDNA_edge_species_df

```

#Species Comparisons
```{r}
#common_species
intersect(common_species_mpa$Species,common_species_nps)
#10 species in common, 
setdiff(common_species_nps,common_species_mpa$Species)

#MPA species  NPS
mpa_species_unique_nps
intersect(eDNA_mpa_species_all$Species,mpa_species_unique_nps)

intersect(eDNA_mpa_species_all$Species,pp_nps_df$Species)
setdiff(pp_nps_df$Species,eDNA_mpa_species_all$Species)

#only ones not detected were 4 that have no barcode/sebastes

#Outside
intersect(eDNA_outside_species_df$Species,ped_nps_df$Species)
setdiff(ped_nps_df$Species,eDNA_outside_species_df$Species)
# only one not detected missing barcode

#Edge
intersect(eDNA_edge_species_df$Species,lsc_nps_df$Species)
setdiff(lsc_nps_df$Species,eDNA_edge_species_df$Species)
#did not detect Lythrypnus zebra

mpa_species_df 


ped_nps_df <- as.data.frame(ped_nps)
lsc_nps_df <- as.data.frame(lsc_nps)
pp_nps_df <- as.data.frame(pp_nps)

get_taxa_unique(physeq_obj.occ_fish,"Species") -> eDNA_step2_species

nps_all_unique

setdiff(nps_all_unique, eDNA_step2_species)
setdiff(eDNA_step2_species, nps_all_unique)

ca_fish_list <- read.table("/Users/zackgold/Documents/UCLA_phd/Projects/California/reference_db/MS/data/fish_species_lists/miller_allen_combo_032620.csv", header = 1, sep = ",", stringsAsFactors = F)

ca_fish_list$Miller_Lea_Combo_03262020 %>% unique() -> miller_list

intersect(setdiff(eDNA_step2_species, nps_all_unique),miller_list) -> eDNa_add_ca_species
setdiff(setdiff(eDNA_step2_species, nps_all_unique),miller_list)

nps2005_fish_list <- read.table("/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/nps_all_species.txt", header = 1, sep = "\t", stringsAsFactors = F)

setdiff(setdiff(eDNA_step2_species, nps_all_unique),nps2005_fish_list$NPS_species)

intersect(setdiff(eDNA_step2_species, nps_all_unique),nps2005_fish_list$NPS_species)

setdiff(eDNa_add_ca_species,nps2005_fish_list$NPS_species)



kable(eDNA_step2_species)
```


#Functional Traits

```{r}
functional_traits <- read.table("/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/functional_traits_all_20200409_2_species_only.csv", header = 1, sep = ",", stringsAsFactors = F)

 functional_traits %>%  as.tibble() %>% 
   filter(., Species !="") -> functional_traits_species_only
   
   functional_traits_species_only %>% 
   group_by(Species_found.pre) %>% tally()
 
  functional_traits_species_only %>%  
    filter(., Species_found.pre=="Common_species") %>% 
   group_by(Habitat) %>% tally()
  
  functional_traits_species_only %>%  
    filter(., Species_found.pre=="Common_species") %>% 
   filter(., Habitat =="pelagic-oceanic")
  
   functional_traits_species_only %>%  
    filter(., Species_found.pre!="Common_species") %>% 
   group_by(Habitat) %>% tally()
  
  functional_traits %>%  as.tibble() %>% 
    filter(., Species_found.pre=="Common_species") %>% 
   filter(., Habitat =="pelagic-oceanic")
  53-21
32/53

functional_traits %>%  as.tibble() %>% 
    filter(., MPA.pre=="0") %>% 
   group_by(Habitat) %>% tally()

43-15
28/43

 functional_traits %>%  as.tibble() %>% 
    filter(., MPA.pre=="0") %>% 
   group_by(Habitat) %>%
   filter(., Habitat !="rockyreef")
```

```{r}

functional_traits %>%  as.tibble() %>% 
  filter(., Species_found.post !="Empty") %>%  filter(.,Species_found.post!="") -> functional_traits_species_only_post
   
   functional_traits_species_only_post %>% 
   group_by(Species_found.post)  %>% tally()
 
  functional_traits_species_only_post %>%  
    filter(., Species_found.post=="Common_species") %>% 
   group_by(Habitat) %>% tally()
  
  functional_traits_species_only_post %>%  
    filter(., Species_found.post=="Common_species") %>% 
   filter(., Habitat =="pelagic-neritic")
  

   functional_traits_species_only_post %>%  
    filter(., Species_found.post!="Common_species") %>% 
   group_by(Habitat) %>% tally()
  
 functional_traits_species_only_post %>% 
    filter(., Species_found.post!="Common_species") %>% 
   filter(., Habitat =="rockyreef")
  53-21
32/53



```

```{r}
functional_traits_fish_occ <- read.table("/Users/zackgold/Documents/UCLA_phd/Projects/California/General_Channel_Islands/MPA_test_data/input/2020320_analysis/analysis_20200330/functional_traits_all_042420_species_only.csv", header = 1, sep = ",", stringsAsFactors = F)
functional_traits_fish_occ


  
   functional_traits_fish_occ %>% as.tibble() %>% 
   group_by(Species_found.post)  %>% tally()
 
  functional_traits_fish_occ   %>% as.tibble() %>% 
    filter(., Species_found.post=="Common_species") %>% 
   group_by(Habitat) %>% tally()
  
  functional_traits_fish_occ %>%  
    filter(., Species_found.post=="Common_species") %>% 
   filter(., Habitat =="pelagic-neritic")
  

   functional_traits_fish_occ %>%  
    filter(., Species_found.post!="Common_species") %>% 
   group_by(Habitat) %>% tally()
  
 functional_traits_fish_occ %>% as.tibble() %>% 
    filter(., Species_found.post!="Common_species") %>% 
   filter(., Habitat =="rockyreef")
 
 functional_traits_fish_occ %>% as.tibble() %>% 
    filter(., Species_found.post=="Outside_species_unique") 

  functional_traits_fish_occ %>% as.tibble() %>% 
    filter(., Species_found.post=="Edge_species_unique") 
  
    functional_traits_fish_occ %>% as.tibble() %>% 
    filter(., Species_found.post=="Outside_edge_species_common") 
    
        functional_traits_fish_occ %>% as.tibble() %>% 
    filter(., Species_found.post=="Mpa_species_unique") 
        
                functional_traits_fish_occ %>% as.tibble() %>% 
    filter(., Species_found.post=="Edge_mpa_species_common") 
                
                        
                functional_traits_fish_occ %>% as.tibble() %>% 
    filter(., Species_found.post=="Outside_mpa_species_common") 
  
 13/28
```

